### 2017-05-22 sig-alternate.tex
Initial ShareLaTeX Import

% This is "sig-alternate.tex" V2.0 May 2012
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate}

\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
Format\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author

}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
The tremendous amount of user-generated contents, such as the questions about symptoms and diseases being asked by a user in online forums, or blog posts about dietary and fitness, are potential sources for enriching knowledge in medical document retrieval and health-related text mining applications. Understanding those various contents is simply not a trivial task. Reducing the complex characteristics of contents, including but not limited to linguistic variations, into structured information can help the text interpretation process. A common approach is to extract medical terms from each document using available tools, such as medical entity recognizer. However, we argue that there are many missing pieces of information when we rely only on medical entities or keywords as main information. Hence, we use keyphrases extraction techniques to extract more important information about the concept of the document. Previous works in keyphrases extraction mostly focused on a general domain, long and formal written documents. These methods perform poorly when being applied to user-generated contents and medical documents. In this work, we propose deep bi-directional recurrent network and convolutional neural network as a model for extracting keyphrases. Furthermore, we leveraged word embedding, medical concepts from a knowledge base, and linguistic components as our features. The proposed algorithm achieved F1 score of 82.41\%. This result outperforms state of the art system for extracting keyphrases using a statistical model.

\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging}

\section{Introduction}
There are tremendous amount of user-generated contents about medical information through the internet. As a result, there is a growing need for enriching medical-related knowledge, for which it can be very valuable for several tasks, such as medical document retrieval, medical question answering, and health-related text mining applications. However, understanding those various health-related contents, especially from social media, is simply not a trivial task since they are written in free text format (i.e. unstructured format), and often prone to grammatical and typographical glitches. Therefore, reducing the complex characteristics of the textual contents, including but not limited to linguistic variations, into structured information could be very beneficial for the text interpretation process.

One possible solution is to extract medical terms that represents the document they belong to. The common approach is harnessing medical entity recognizer. However, we argue that there are many missing pieces of information when we merely rely on medical entities or terminologies as our main information for representing a particular document. In this paper, we present new keyphrases extraction techniques to extract more important information about the concept expressed inside the document. Furthermore, we also propose a new definition of keyphrases, which is based on our observation of health-related documents. Actually, our final goal is to develop medical question answering systems to assist physicians or people obtaining health information. The work presented in this paper is absolutely inline with our goal, since important keyphrases of a question document can be used to formulate a query for the passage retrieval subsystem.

Keyphrases are usually selected phrases or clauses that can capture the main topic of a given document \citep{turney2000learning}. They can provide readers with highly valuable and representative information, such that looking at keyphrases is sufficient to understand the whole body of document. Moreover, keyphrases are important for text summarization, document clustering, and classification task (\citep{classDocumentEkp1}; \citep{qaEkp}; \citep{gong2009improving}). Previous works have shown that using keyphrases to generate queries can improve the quality of question retrieval in medical question answering forum \citep{cao2010automatically}.

Keyphrase extraction methods have been mostly using statistical approach (\cite{sparck1972statistical}, \citep{zhang2007comparative}, \citep{rake}, \cite{mihalcea2004textrank}) and supervised learning approach (\citep{witten1999kea}; \citep{medelyan2009human}; \citep{marujoMAUI}). The statistical approach often involves keyword candidate selection and candidate's property calculation. The "keywordness" value of a candidate phrase is usually scored based on its typical length as well as frequency in which document it appears \citep{rake}. While the statistical approach is very efficient to generate keyphrases, our experiments showed that it performs poorly on user generated contents and short documents. The other approach is based on supervised learning, there are two common approach in supervised learning: classification and sequence labeling. In classification approach, candidate keyphrases are extracted using statistical \citep{sparck1972statistical} or language model \citep{ekpNeuralNetworks}. Then, the candidate keyphrases are classified whether a candidate is a keyphrase or not by using a pretrained model. However, classification approach cannot capture semantic relationship between words in a document \citep{surveyPopulerTerbaruEkp}.  In sequence labeling approach,  like the one proposed by \citep{cao2010automatically} and \cite{zhang2008automatic}. They define keyphrase extraction task as a sequence labeling task, in which each word in the document can have two possible labels: keyword or non-keyword. The method they proposed worked well by outperforming unsupervised approach. However, synonym and ambiguity words cannot be handled properly \citep{zhang2008automatic}

In our work, we use the same approach as \cite{cao2010automatically} which treats keyphrase extraction as a sequence labeling task. In our experiment, we employed and combined various deep learning architectures, such as convolutional neural networks and bi-directional long short-term memory networks, to exploit high level features between neighboring word positions. To improve the quality of our model, we leverage several new hand-crafted features that can handle our keyphrase extraction problems in medical user-generated content, such as word importance and word stickiness features. The word importance feature is enable to rank words in a document by their importance value. The more important a word is to the content of document, the higher its "keywordness" value would seem to be. In addition, we also propose word stickiness feature to make our model constructs keyphrases better.

We also employed pre-trained word embedding to incorporate contextual, semantic, and syntactic information of a word. For example, we found that pre-trained word embedding can handle slang words and abbreviations by giving their word vectors closer to the vectors of their canonical forms. Finally, to evaluate the effectiveness of our model, we collected and manually annotated data from Indonesian medical forum questions, such as alodokter, health detik, doktergratis, dokter.id, doktersehat, klikdokter \footnote{www.alodokter.com, health.detik.com, www.dokter.id, www.doktersehat.com, www.klikdokter.com}. After that, the dataset was used for both training and testing our computational models. For our baseline, we use RAKE  \citep{rake}, which is the current state of the art model for extracting keyphrases.

This paper is organized as follows.  In section 2 we discuss related works in keyphrase extraction. In section 3, the proposed keyphrase extraction method has been discussed. We present the evaluation and the experimental results in section 4.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning,
clark:pct, braams:babel, herlihy:methodology},
conference proceedings \cite{clark:pct} or
books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed or supported.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps}
and \textbf{.ps} files to be displayable with \LaTeX.  More
details on each of these is found in the \textit{Author's Guide}.

\begin{figure}
\centering
\epsfig{file=fly.eps}
\caption{A sample black and white graphic (.eps format).}
\end{figure}

\begin{figure}
\centering
\epsfig{file=fly.eps, height=1in, width=1in}
\caption{A sample black and white graphic (.eps format)
that has been resized with the \texttt{epsfig} command.}
\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.
and don't forget to end the environment with
{figure*}, not {figure}!

\begin{figure*}
\centering
\epsfig{file=flies.eps}
\caption{A sample black and white graphic (.eps format)
that needs to span two columns of text.}
\end{figure*}

Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
used; use
the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
commands as appropriate for the different file types.

\begin{figure}
\centering
\psfig{file=rosette.ps, height=1in, width=1in,}
\caption{A sample black and white graphic (.ps format) that has
been resized with the \texttt{psfig} command.}
\vskip -6pt
\end{figure}

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The sig-alternate.cls file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
%\balancecolumns % GM June 2007
% That's all folks!
\end{document}

### 2017-05-22 sample-sigconf.tex
Pindah Git

--- 2017-05-22 sig-alternate.tex
@@
-% This is "sig-alternate.tex" V2.0 May 2012
-% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
-%
-% This example file demonstrates the use of the 'sig-alternate.cls'
-% V2.5 LaTeX2e document class file. It is for those submitting
-% articles to ACM Conference Proceedings WHO DO NOT WISH TO
-% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
-% The 'sig-alternate.cls' file will produce a similar-looking,
-% albeit, 'tighter' paper resulting in, invariably, fewer pages.
-%
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V2.5) produces:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) NO page numbers
-%
-% as against the acm_proc_article-sp.cls file which
-% DOES NOT produce 1) thru' 3) above.
-%
-% Using 'sig-alternate.cls' you have control, however, from within
-% the source .tex file, over both the CopyrightYear
-% (defaulted to 200X) and the ACM Copyright Data
-% (defaulted to X-XXXXX-XX-X/XX/XX).
-% e.g.
-% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
-% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
-%
-% ---------------------------------------------------------------------------------------------------------------
-% This .tex source is an example which *does* use
-% the .bib file (from which the .bbl file % is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission, you *NEED* to 'insert'
-% your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% ================= IF YOU HAVE QUESTIONS =======================
-% Questions regarding the SIGS styles, SIGS policies and
-% procedures, Conferences etc. should be sent to
-% Adrienne Griscti (griscti@acm.org)
-%
-% Technical questions _only_ to
-% Gerald Murray (murray@hq.acm.org)
-% ===============================================================
-%
-% For tracking purposes - this is V2.0 - May 2012
+\documentclass[sigconf]{acmart}
 
-\documentclass{sig-alternate}
+\usepackage{booktabs} % For formal tables
+
+% Copyright
+%\setcopyright{none}
+%\setcopyright{acmcopyright}
+%\setcopyright{acmlicensed}
+\setcopyright{rightsretained}
+%\setcopyright{usgov}
+%\setcopyright{usgovmixed}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
+
+% DOI
+\acmDOI{10.475/123_4}
+
+% ISBN
+\acmISBN{123-4567-24-567/08/06}
+
+%Conference
+\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
+  Paso, Texas USA} 
+\acmYear{1997}
+\copyrightyear{2016}
+
+\acmPrice{15.00}
 
 \begin{document}
-%
-% --- Author Metadata here ---
-\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
-%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
-% --- End of Author Metadata ---
 
-\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
-Format\titlenote{(Produces the permission block, and
-copyright information). For use with
-SIG-ALTERNATE.CLS. Supported by ACM.}}
-\subtitle{[Extended Abstract]
-\titlenote{A full version of this paper is available as
-\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-\LaTeX$2_\epsilon$\ and BibTeX} at
-\texttt{www.acm.org/eaddress.htm}}}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
+\title{SIG Proceedings Paper in LaTeX Format}
+\titlenote{Produces the permission block, and
+  copyright information}
+\subtitle{Extended Abstract}
+\subtitlenote{The full version of the author's guide is available as
+  \texttt{acmart.pdf} document}
 
-\numberofauthors{8} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
-\author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
+% The default list of authors is too long for headers}
+\renewcommand{\shortauthors}{B. Trovato et al.}
 
-}
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-\date{30 July 1999}
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
-
-\maketitle
 \begin{abstract}
@@
 This result outperforms state of the art system for extracting keyphrases using a statistical model.
-
 \end{abstract}
 
-% A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+%
+% The code below should be generated by the tool at
+% http://dl.acm.org/ccs.cfm
+% Please copy and paste the code instead of the example below. 
+%
+\begin{CCSXML}
+<ccs2012>
+ <concept>
+  <concept_id>10010520.10010553.10010562</concept_id>
+  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+  <concept_significance>500</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10010520.10010575.10010755</concept_id>
+  <concept_desc>Computer systems organization~Redundancy</concept_desc>
+  <concept_significance>300</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10010520.10010553.10010554</concept_id>
+  <concept_desc>Computer systems organization~Robotics</concept_desc>
+  <concept_significance>100</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10003033.10003083.10003095</concept_id>
+  <concept_desc>Networks~Network reliability</concept_desc>
+  <concept_significance>100</concept_significance>
+ </concept>
+</ccs2012>  
+\end{CCSXML}
 
-\terms{Theory}
+\ccsdesc[500]{Computer systems organization~Embedded systems}
+\ccsdesc[300]{Computer systems organization~Redundancy}
+\ccsdesc{Computer systems organization~Robotics}
+\ccsdesc[100]{Networks~Network reliability}
 
@@
 
-\section{Introduction}
-There are tremendous amount of user-generated contents about medical information through the internet.
-As a result, there is a growing need for enriching medical-related knowledge, for which it can be very valuable for several tasks, such as medical document retrieval, medical question answering, and health-related text mining applications.
-However, understanding those various health-related contents, especially from social media, is simply not a trivial task since they are written in free text format (i.e.
-unstructured format), and often prone to grammatical and typographical glitches.
-Therefore, reducing the complex characteristics of the textual contents, including but not limited to linguistic variations, into structured information could be very beneficial for the text interpretation process.
+\maketitle
 
-One possible solution is to extract medical terms that represents the document they belong to.
-The common approach is harnessing medical entity recognizer.
-However, we argue that there are many missing pieces of information when we merely rely on medical entities or terminologies as our main information for representing a particular document.
-In this paper, we present new keyphrases extraction techniques to extract more important information about the concept expressed inside the document.
-Furthermore, we also propose a new definition of keyphrases, which is based on our observation of health-related documents.
-Actually, our final goal is to develop medical question answering systems to assist physicians or people obtaining health information.
-The work presented in this paper is absolutely inline with our goal, since important keyphrases of a question document can be used to formulate a query for the passage retrieval subsystem.
+\input{samplebody-conf}
 
-Keyphrases are usually selected phrases or clauses that can capture the main topic of a given document \citep{turney2000learning}.
-They can provide readers with highly valuable and representative information, such that looking at keyphrases is sufficient to understand the whole body of document.
-Moreover, keyphrases are important for text summarization, document clustering, and classification task (\citep{classDocumentEkp1}; \citep{qaEkp}; \citep{gong2009improving}).
-Previous works have shown that using keyphrases to generate queries can improve the quality of question retrieval in medical question answering forum \citep{cao2010automatically}.
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{sigproc}
 
-Keyphrase extraction methods have been mostly using statistical approach (\cite{sparck1972statistical}, \citep{zhang2007comparative}, \citep{rake}, \cite{mihalcea2004textrank}) and supervised learning approach (\citep{witten1999kea}; \citep{medelyan2009human}; \citep{marujoMAUI}).
-The statistical approach often involves keyword candidate selection and candidate's property calculation.
-The "keywordness" value of a candidate phrase is usually scored based on its typical length as well as frequency in which document it appears \citep{rake}.
-While the statistical approach is very efficient to generate keyphrases, our experiments showed that it performs poorly on user generated contents and short documents.
-The other approach is based on supervised learning, there are two common approach in supervised learning: classification and sequence labeling.
-In classification approach, candidate keyphrases are extracted using statistical \citep{sparck1972statistical} or language model \citep{ekpNeuralNetworks}.
-Then, the candidate keyphrases are classified whether a candidate is a keyphrase or not by using a pretrained model.
-However, classification approach cannot capture semantic relationship between words in a document \citep{surveyPopulerTerbaruEkp}.
-In sequence labeling approach,  like the one proposed by \citep{cao2010automatically} and \cite{zhang2008automatic}.
-They define keyphrase extraction task as a sequence labeling task, in which each word in the document can have two possible labels: keyword or non-keyword.
-The method they proposed worked well by outperforming unsupervised approach.
-However, synonym and ambiguity words cannot be handled properly \citep{zhang2008automatic}
-
-In our work, we use the same approach as \cite{cao2010automatically} which treats keyphrase extraction as a sequence labeling task.
-In our experiment, we employed and combined various deep learning architectures, such as convolutional neural networks and bi-directional long short-term memory networks, to exploit high level features between neighboring word positions.
-To improve the quality of our model, we leverage several new hand-crafted features that can handle our keyphrase extraction problems in medical user-generated content, such as word importance and word stickiness features.
-The word importance feature is enable to rank words in a document by their importance value.
-The more important a word is to the content of document, the higher its "keywordness" value would seem to be.
-In addition, we also propose word stickiness feature to make our model constructs keyphrases better.
-
-We also employed pre-trained word embedding to incorporate contextual, semantic, and syntactic information of a word.
-For example, we found that pre-trained word embedding can handle slang words and abbreviations by giving their word vectors closer to the vectors of their canonical forms.
-Finally, to evaluate the effectiveness of our model, we collected and manually annotated data from Indonesian medical forum questions, such as alodokter, health detik, doktergratis, dokter.id, doktersehat, klikdokter \footnote{www.alodokter.com, health.detik.com, www.dokter.id, www.doktersehat.com, www.klikdokter.com}.
-After that, the dataset was used for both training and testing our computational models.
-For our baseline, we use RAKE  \citep{rake}, which is the current state of the art model for extracting keyphrases.
-
-This paper is organized as follows.
-In section 2 we discuss related works in keyphrase extraction.
-In section 3, the proposed keyphrase extraction method has been discussed.
-We present the evaluation and the experimental results in section 4.
-
-\section{The {\secit Body} of The Paper}
-Typically, the body of a paper is organized
-into a hierarchical structure, with numbered or unnumbered
-headings for sections, subsections, sub-subsections, and even
-smaller sections.  The command \texttt{{\char'134}section} that
-precedes this paragraph is part of such a
-hierarchy.\footnote{This is the second footnote.  It
-starts a series of three footnotes that add nothing
-informational, but just give an idea of how footnotes work
-and look. It is a wordy one, just so you see
-how a longish one plays out.} \LaTeX\ handles the numbering
-and placement of these headings for you, when you use
-the appropriate heading commands around the titles
-of the headings.  If you want a sub-subsection or
-smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both
-numbered and unnumbered headings will appear throughout the
-balance of this sample document.
-
-Because the entire article is contained in
-the \textbf{document} environment, you can indicate the
-start of a new paragraph with a blank line in your
-input file; that is why this sentence forms a separate paragraph.
-
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with
-the command \texttt{{\char'134}textit}; emboldening with the
-command \texttt{{\char'134}textbf}
-and typewriter-style (for instance, for computer code) with
-\texttt{{\char'134}texttt}.  But remember, you do not
-have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your
-article; for instance, the heading of this subsection will
-be in a sans serif\footnote{A third footnote, here.
-Let's make this a rather short one to
-see how it looks.} typeface, but that is handled by the
-document class file. Take care with the use
-of\footnote{A fourth, and last, footnote.}
-the curly braces in typeface changes; they mark
-the beginning and end of
-the text that is to be in the different typeface.
-
-You can use whatever symbols, accented characters, or
-non-English characters you need anywhere in your document;
-you can find a complete list of what is
-available in the \textit{\LaTeX\
-User's Guide}\cite{Lamport:LaTeX}.
-
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
-
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-construction or with the short form \texttt{\$. . .\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space
-from the text and centered horizontally -- is produced
-by the \textbf{equation} environment. An unnumbered display
-equation is produced by the \textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning,
-clark:pct, braams:babel, herlihy:methodology},
-conference proceedings \cite{clark:pct} or
-books \cite{salas:calculus, Lamport:LaTeX} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file \cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
-
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
-
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed or supported.
-
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
-
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
-
-\begin{table*}
-\centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
-
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
-
-This sample document contains examples of \textbf{.eps}
-and \textbf{.ps} files to be displayable with \LaTeX.  More
-details on each of these is found in the \textit{Author's Guide}.
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps}
-\caption{A sample black and white graphic (.eps format).}
-\end{figure}
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps, height=1in, width=1in}
-\caption{A sample black and white graphic (.eps format)
-that has been resized with the \texttt{epsfig} command.}
-\end{figure}
-
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption.
-and don't forget to end the environment with
-{figure*}, not {figure}!
-
-\begin{figure*}
-\centering
-\epsfig{file=flies.eps}
-\caption{A sample black and white graphic (.eps format)
-that needs to span two columns of text.}
-\end{figure*}
-
-Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
-used; use
-the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
-commands as appropriate for the different file types.
-
-\begin{figure}
-\centering
-\psfig{file=rosette.ps, height=1in, width=1in,}
-\caption{A sample black and white graphic (.ps format) that has
-been resized with the \texttt{psfig} command.}
-\vskip -6pt
-\end{figure}
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
-
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
-
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
-
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to
-use the \texttt{{\char'134}newdef} command to create a
-new form, you might think you can
-use \TeX's \texttt{{\char'134}def} to create a
-new command: \textit{Please refrain from doing this!}
-Remember that your \LaTeX\ source code is primarily intended
-to create camera-ready copy, but may be converted
-to other forms -- e.g. HTML. If you inadvertently omit
-some or all of the \texttt{{\char'134}def}s recompilation will
-be, to say the least, problematic.
-
-\section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
-%\end{document}  % This is where a 'short' article might terminate
-
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
-
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Headings in Appendices}
-The rules about hierarchical headings discussed above for
-the body of the article are different in the appendices.
-In the \textbf{appendix} environment, the command
-\textbf{section} is used to
-indicate the start of each Appendix, with alphabetic order
-designation (i.e. the first is A, the second B, etc.) and
-a title (if you include one).  So, if you need
-hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this
-document in Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{Acknowledgments}
-\subsection{Additional Authors}
-This section is inserted by \LaTeX; you do not insert it.
-You just add the names and information in the
-\texttt{{\char'134}additionalauthors} command at the start
-of the document.
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the ~.bbl file.  Insert that ~.bbl file into
-the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-% This next section command marks the start of
-% Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-The sig-alternate.cls file itself is chock-full of succinct
-and helpful comments.  If you consider yourself a moderately
-experienced to expert user of \LaTeX, you may find reading
-it useful but please remember not to change it.
-%\balancecolumns % GM June 2007
-% That's all folks!
 \end{document}

### 2017-05-22 samplebody-conf.tex
Pindah Git

\section{Introduction}

There are tremendous amount of user-generated contents about medical information through the internet. As a result, there is a growing need for enriching medical-related knowledge, for which it can be very valuable for several tasks, such as medical document retrieval, medical question answering, and health-related text mining applications. However, understanding those various health-related contents, especially from social media, is simply not a trivial task since they are written in free text format (i.e. unstructured format), and often prone to grammatical and typographical glitches. Therefore, reducing the complex characteristics of the textual contents, including but not limited to linguistic variations, into structured information could be very beneficial for the text interpretation process.

One possible solution is to extract medical terms that represents the document they belong to. The common approach is harnessing medical entity recognizer. However, we argue that there are many missing pieces of information when we merely rely on medical entities or terminologies as our main information for representing a particular document. In this paper, we present new keyphrases extraction techniques to extract more important information about the concept expressed inside the document. Furthermore, we also propose a new definition of keyphrases, which is based on our observation of health-related documents. Actually, our final goal is to develop medical question answering systems to assist physicians or people obtaining health information. The work presented in this paper is absolutely inline with our goal, since important keyphrases of a question document can be used to formulate a query for the passage retrieval subsystem.

Keyphrases are usually selected phrases or clauses that can capture the main topic of a given document \cite{turney2000learning}. They can provide readers with highly valuable and representative information, such that looking at keyphrases is sufficient to understand the whole body of document. Moreover, keyphrases are important for text summarization, document clustering, and classification task (\cite{classDocumentEkp1}; \cite{qaEkp}; \cite{gong2009improving}). Previous works have shown that using keyphrases to generate queries can improve the quality of question retrieval in medical question answering forum \cite{cao2010automatically}.

Keyphrase extraction methods have been mostly using statistical approach (\cite{sparck1972statistical} \cite{zhang2007comparative} \cite{rake} \cite{mihalcea2004textrank}) and supervised learning approach (\cite{witten1999kea} \cite{medelyan2009human} \cite{marujoMAUI}). The statistical approach often involves keyword candidate selection and candidate's property calculation. The "keywordness" value of a candidate phrase is usually scored based on its typical length as well as frequency in which document it appears \cite{rake}. While the statistical approach is very efficient to generate keyphrases, our experiments showed that it performs poorly on user generated contents and short documents. The other approach is based on supervised learning, there are two common approach in supervised learning: classification and sequence labeling. In classification approach, candidate keyphrases are extracted using statistical \cite{sparck1972statistical} or language model \cite{ekpNeuralNetworks}. Then, the candidate keyphrases are classified whether a candidate is a keyphrase or not by using a pretrained model. However, classification approach cannot capture semantic relationship between words in a document \cite{surveyPopulerTerbaruEkp}.  In sequence labeling approach,  like the one proposed by \cite{cao2010automatically} and \cite{zhang2008automatic}. They define keyphrase extraction task as a sequence labeling task, in which each word in the document can have two possible labels: keyword or non-keyword. The method they proposed worked well by outperforming unsupervised approach. However, synonym and ambiguity words cannot be handled properly \cite{zhang2008automatic}.

In our work, we use the same approach as \cite{cao2010automatically} which treats keyphrase extraction as a sequence labeling task. In our experiment, we employed and combined various deep learning architectures, such as convolutional neural networks and bi-directional long short-term memory networks, to exploit high level features between neighboring word positions. To improve the quality of our model, we leverage several new hand-crafted features that can handle our keyphrase extraction problems in medical user-generated content, such as word importance and word stickiness features. The word importance feature is enable to rank words in a document by their importance value. The more important a word is to the content of document, the higher its "keywordness" value would seem to be. In addition, we also propose word stickiness feature to make our model constructs keyphrases better.

We also employed pre-trained word embedding to incorporate contextual, semantic, and syntactic information of a word. For example, we found that pre-trained word embedding can handle slang words and abbreviations by giving their word vectors closer to the vectors of their canonical forms. Finally, to evaluate the effectiveness of our model, we collected and manually annotated data from Indonesian medical forum questions, such as alodokter, health detik, doktergratis, dokter.id, doktersehat, klikdokter \footnote{www.alodokter.com, health.detik.com, www.dokter.id, www.doktersehat.com, www.klikdokter.com}. After that, the dataset was used for both training and testing our computational models. For our baseline, we use RAKE  \cite{rake}, which is the current state of the art model for extracting keyphrases.

This paper is organized as follows.  In section 2 we discuss related works in keyphrase extraction. In section 3, the proposed keyphrase extraction method has been discussed. We present the evaluation and the experimental results in section 4.

\section{Related Works}
In general, keyphrase extraction methods can be divided into two groups: unsupervised ranking (statistical) approach and supervised machine learning approach. For the unsupervised line of research, keyphrase extraction is formulated as a ranking problem, in which each candidate keyphrase is assigned a score that represents its keywordness value. Furthermore, this kind of approach does not require training data, which is often very difficult to obtain. On the other hand, supervised machine learning approach requires training data that contains a collection of documents with their labeled keywords. Using this approach, keyphrase extraction is usually treated as a classification or sequence labeling task in the level of words or phrases. The first step of this approach generates candidate keyphrases from a particular document. Finally, every candidate keyphrase in the document will be classified as either a keyphrase or non-keyphrase. Recently, a well-known supervised approach for keyphrase extraction is based on sequence labeling problem (\cite{zhang2008automatic}\cite{cao2010automatically}\cite{zhang2016keyphrase}). The assumption behind this model is that the decision on whether a particular word serves as a keyword is affected by the information from its neighboring word positions.

In the work of \cite{sparck1972statistical}, they leverage TF-IDF to get the most significant words. Specifically, they utilize term frequency and the inverse of document frequency to rank terms in the document. First, this Rapid Automatic Keywords Extraction \cite{rake} uses stopwords to split a document into several candidate keyphrases. All candidates will be ranked by the degrees and frequencies of all words inside them. Finally, the rank points of each candidate is obtained by summing over all degrees and frequencies of all words contained in each keyphrase. RAKE is proven to be successful for extracting keyphrases in special documents such as paper and article \cite{rake}.

There is also a popular graph-based approach, namely TextRank (U), i.e., a modified PageRank algorithm to extract keyphrases from a document. They exploit word co-occurrence information to build a document graph, in which a word serves as a node and co-occurence information determines an edge between two nodes (words). After they build the graph, they actually run PageRank algorithm to determine the keywordness score for each node in the graph. A word with high PageRank value denotes that its related concept can be found in many location inside the document, which means that it is a good candidate for keyword. After that, keyphrases can be obtained using post-processing step that may combine contiguous candidates into one keyphrase.

One of the earlier supervised approaches in the problem of keyphrase extraction is KEA \cite{witten1999kea}. KEA uses tf-idf and first occurrence of the term to identify candidate keyphrases. They use a machine-learning algorithm (i.e., Naive Bayes) to predict whether or not a candidate is a good keyphrase. \cite{medelyan2009human} developed a system called MAUI that can extract keyphrases using trained corpus and controlled vocabulary. MAUI itself is an improvement to the aforementioned supervised model, KEA. Furthermore, \cite{marujoMAUI} use word embedding and brown clustering as features. Their experiment result had shown that the proposed features and MAUI performs better than statistical methods, such as simple tf-idf approach.

The utilization of neural networks is also quite popular in the recent years. \cite{ekpNeuralNetworks} uses Feed Forward Neural Networks to classify candidate keyphrases. To extract candidate keyphrases, they use POS tag information for classifying all words in the document. Then, Deterministic Finite Automation (DFA) is used to extract noun phrases as candidate keyphrases. Furthermore, deep neural networks is also employed for extracting keyphrase, like the one proposed by \cite{zhang2016keyphrase}, that uses joint Recurrent Neural Networks (RNNs) layer to capture keyphrase sequences in microblogs. The research had shown that RNN is very effective to extract keyword.

Unfortunately, there are limited works regarding the task of keyphrase extraction in medical domain. \cite{ekpMedicalDocumentHybrid} use a hybrid medical knowledge base and statistical approach to extract keyphrases from medical articles. They use stopwords to split candidate keyphrases, then candidates are ranked with two aspects: PF-IDF (Phrase Frequency * Inverse Document Frequency) and domain knowledge which is extracted from medical article. In terms of medical social media content, \cite{cao2010automatically} use Conditional Random Fields (CRFs) for extracting keywords from medical questions in online health-forum. They use information, such as word location and length as features in their experiments.

\section{METHODOLOGY}
\subsection{DATA AND ANNOTATION}
To analyze the effectiveness of our model for keyphrase extraction in user-generated medical domain, we constructed an evaluation dataset. A a number of questions was gathered from Indonesian medical question answering forum. The data was crawled by \cite{skripsiKakRadit} and \cite{skripsiWahid} in their experiment. Generally, we gathered 416 question-answer pairs from \cite{skripsiKakRadit} and \cite{skripsiWahid}. We decided to use the same question-answers pairs to observe our keyphrases and medical entities that has been annotated by them. In addition, system for recognizing medical entities is not fully build, by using the same document we can use the annotated medical entities as our feature.

From analyzing these question-answer pairs, we found some noise and unnecessary information. Question and answer have different main topic and focus. Moreover, we are focusing our task for getting user intentions and needs in our experiment. Based on that problem, we only use questions by users and remove answers by the doctors because it would be a better representation of user intentions and needs. There is also unnecessary information such as URL and email. We replace URL with “URL”  and email with “email” since we were focusing on textual content. Moreover, we also removed ads and spam in the data we gathered.

Because we want to process all the questions by users, we tokenize every question in our data. The tokenization process included separating alphanumeric with non-alphanumeric. Then separating alphanumeric with numeric.

To evaluate the quality of our model. We manually annotated or data to label keyphrases in 416 questions. In this work, we use "IOB" tagging scheme to label every word \cite{collobert2011natural}. In Table X, we give an example sequence with labels for each word. The statistical information of the dataset can be seen in Table X

\subsection{TASK DEFINITIONS}
\subsection{MODEL ARCHITECTURE}
We process the sequences word by word. Features are extracted from every word as the input representation of the model. The output for this words are label which describe a word is either part of keyphrase or not.

To give our model a better insight of context, we introduce Convolutional Neural Networks (CNNs) to capture context from three adjacent words.  From our observation, to know whether a word is part of keyphrase or not, we need to know the context of the word itself. For example, “Doc, i have a frequent back pain. What happen?”. The keyphrase for previous example is “frequent back pain”. In order to know that “back” is part of keyphrase, we need information from the word “frequent” which give an intensity of a symptom and “pain” which refer to “back pain” as main term. With CNNs, we argue that our model can capture the surrounding information of a word.

To get a better inference, information from the past and future sequences can be integrated. This approach is proven effective  in sequence labeling task such as semantic role labeling \cite{SMRzhou2015end} and named entity recognition \cite{ma2016end}. Hence, we utilized  bi-directional LSTM (B-LSTM) for extracting structural knowledge by processing sequences both forward and backward.
To perform the sequence tagging task, we build a fully connected layer in the top of our model. This layer will classify the output of our model with softmax activation function.

We also experimented on customizing the way we input the features underneath our aforementioned networks. Instead of concatenating all feature into one vector, we tried to give weight for every feature we have. We argue that each feature have different contribution to the model. In order to do so, we create a new layer underneath our model to do the weighting scenario. The following equation to weight all feature can be seen in below:
\begin{equation}
	Z =  tanh(W _{1}*F_{1} + W_{2}*F_{2} + .. + W_{n}*F_{n})
\end{equation}
Where $W_{i}$ are the weight for each feature and $F_{i}$ are the extracted feature in vector form.
\section{EXPERIMENTS}
We mainly evaluated and analyzed our system on 416 manually annotated Indonesian medical questions.
\subsubsection{FEATURE ABLATION STUDY}
In this part, perform a feature ablation study. By considering all the features, and then removing one of these features, we want to estimate the importance of the features. To the experiment. We use 80\% as training set, and 20\% as a testing set. We used precision (P), recall (R), and F1-score (F1) as evaluation metrics. Table X show the experimental result. Then, we use LSTM as evaluation model because it is the most simple architecture. These are the following features we proposed: word stickiness (Ws), word abbreviation and acronym (Wa), Medical Entities (Me), Word Location (Wp), Word Length (Wl), Word Importance (Wi), POS tag (Pt), Medical Dictionary (Md).

\begin{table*}
	\caption{Feature Ablation Study Result}
	\label{tab:ablation}
	\begin{tabular}{cccl}
		\toprule
		Features&Precision&Recall&F-Measure\\
		\midrule
		Ws + Wa + Me + Wp + Wl + Wi + Pt + Md & 1 in 1,000& For Swedish names&hehe\\
		$\pi$ & 1 in 5& Common in math&hehe\\
		\$ & 4 in 5 & Used in business&hehe\\
		$\Psi^2_1$ & 1 in 40,000& Unexplained usage&hehe\\
		\bottomrule
	\end{tabular}
\end{table*}

The experimental results in Table X shows that every feature has a positive contribution to the model. It is shown by iteratively remove each feature one by one and every time we remove a feature, F-1 score dropped. Hence, we use every feature to train our model in the next experiments.
Table X shows the performances of different methods.
\section{INI CONTOH}
\subsection{Type Changes and {\itshape Special} Characters}

We have already seen several typeface changes in this sample.  You can
indicate italicized words or phrases in your text with the command
\texttt{{\char'134}textit}; emboldening with the command
\texttt{{\char'134}textbf} and typewriter-style (for instance, for
computer code) with \texttt{{\char'134}texttt}.  But remember, you do
not have to indicate typestyle changes when such changes are part of
the \textit{structural} elements of your article; for instance, the
heading of this subsection will be in a sans serif\footnote{Another
  footnote here.  Let's make this a rather long one to see how it
  looks.} typeface, but that is handled by the document class file.
Take care with the use of\footnote{Another footnote.}  the
curly braces in typeface changes; they mark the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or non-English
characters you need anywhere in your document; you can find a complete
list of what is available in the \textit{\LaTeX\ User's Guide}
\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin\,\ldots{\char'134}end}
construction or with the short form \texttt{\$\,\ldots\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX\@; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles~\cite{bowman:reasoning,
clark:pct, braams:babel, herlihy:methodology},
conference proceedings~\cite{clark:pct} or maybe
books \cite{Lamport:LaTeX, salas:calculus} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file~\cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide} by Lamport~\shortcite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
are found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed
output of this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more desirable.
Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

It is strongly recommended to use the package booktabs~\cite{Fear05}
and follow its main principles of typography with respect to tables:
\begin{enumerate}
\item Never, ever use vertical rules.
\item Never use double rules.
\end{enumerate}
It is also a good idea not to overuse horizontal rules.

\subsection{Figures}

Like tables, figures cannot be split across pages; the best placement
for them is typically the top or the bottom of the page nearest their
initial cite.  To ensure this proper ``floating'' placement of
figures, use the environment \textbf{figure} to enclose the figure and
its caption.

This sample document contains examples of \texttt{.eps} files to be
displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
\texttt{.pdf} format.  Note that most modern \TeX\ systems will convert
\texttt{.eps} to \texttt{.pdf} for you on the fly.  More details on
each of these are found in the \textit{Author's Guide}.

\begin{figure}
\includegraphics{fly}
\caption{A sample black and white graphic.}
\end{figure}

\begin{figure}
\includegraphics[height=1in, width=1in]{fly}
\caption{A sample black and white graphic
that has been resized with the \texttt{includegraphics} command.}
\end{figure}

As was the case with tables, you may want a figure that spans two
columns.  To do this, and still to ensure proper ``floating''
placement of tables, use the environment \textbf{figure*} to enclose
the figure and its caption.  And don't forget to end the environment
with \textbf{figure*}, not \textbf{figure}!

\begin{figure*}
\includegraphics{flies}
\caption{A sample black and white graphic
that needs to span two columns of text.}
\end{figure*}

\begin{figure}
\includegraphics[height=1in, width=1in]{rosette}
\caption{A sample black and white graphic that has
been resized with the \texttt{includegraphics} command.}
\end{figure}

\subsection{Theorem-like Constructs}

Other common constructs that may occur in your article are the forms
for logical constructs like theorems, axioms, corollaries and proofs.
ACM uses two types of these constructs:  theorem-like and
definition-like.

Here is a theorem:
\begin{theorem}
  Let $f$ be continuous on $[a,b]$.  If $G$ is
  an antiderivative for $f$ on $[a,b]$, then
  \begin{displaymath}
    \int^b_af(t)\,dt = G(b) - G(a).
  \end{displaymath}
\end{theorem}

Here is a definition:
\begin{definition}
  If $z$ is irrational, then by $e^z$ we mean the
  unique number that has
  logarithm $z$:
  \begin{displaymath}
    \log e^z = z.
  \end{displaymath}
\end{definition}

The pre-defined theorem-like constructs are \textbf{theorem},
\textbf{conjecture}, \textbf{proposition}, \textbf{lemma} and
\textbf{corollary}.  The pre-defined de\-fi\-ni\-ti\-on-like constructs are
\textbf{example} and \textbf{definition}.  You can add your own
constructs using the \textsl{amsthm} interface~\cite{Amsthm15}.  The
styles used in the \verb|\theoremstyle| command are \textbf{acmplain}
and \textbf{acmdefinition}.

Another construct is \textbf{proof}, for example,

\begin{proof}
  Suppose on the contrary there exists a real number $L$ such that
  \begin{displaymath}
    \lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
  \end{displaymath}
  Then
  \begin{displaymath}
    l=\lim_{x\rightarrow c} f(x)
    = \lim_{x\rightarrow c}
    \left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
    = \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
    \frac{f(x)}{g(x)} = 0\cdot L = 0,
  \end{displaymath}
  which contradicts our assumption that $l\neq 0$.
\end{proof}

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e., the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{References}
Generated by bibtex from your \texttt{.bib} file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the \texttt{.bbl} file.  Insert that \texttt{.bbl}
file into the \texttt{.tex} source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}

Of course, reading the source code is always useful.  The file
\path{acmart.pdf} contains both the user guide and the commented
code.

\begin{acks}
  The authors would like to thank Dr. Yuhua Li for providing the
  matlab code of  the \textit{BEPS} method.

  The authors would also like to thank the anonymous referees for
  their valuable comments and helpful suggestions. The work is
  supported by the \grantsponsor{GS501100001809}{National Natural
    Science Foundation of
    China}{http://dx.doi.org/10.13039/501100001809} under Grant
  No.:~\grantnum{GS501100001809}{61273304}
  and~\grantnum[http://www.nnsf.cn/youngscientsts]{GS501100001809}{Young
    Scientsts' Support Program}.

\end{acks}

### 2017-05-22 samplebody-conf.tex
Add tables

@@
 \section{EXPERIMENTS}
-We mainly evaluated and analyzed our system on 416 manually annotated Indonesian medical questions.
-\subsubsection{FEATURE ABLATION STUDY}
+In this section, we analyzed the importance of our features by conducting a feature ablation study. Furthermore, we also established a scenario to test the performance of our model.
+\subsection{Feature Ablation Study}
 In this part, perform a feature ablation study.
@@
 We used precision (P), recall (R), and F1-score (F1) as evaluation metrics.
-Table X show the experimental result.
+Table \ref{tab:ablation} show the experimental result.
 Then, we use LSTM as evaluation model because it is the most simple architecture.
@@
 	\label{tab:ablation}
-	\begin{tabular}{cccl}
+	\begin{tabular}{lccc}
 		\toprule
@@
 		\midrule
-		Ws + Wa + Me + Wp + Wl + Wi + Pt + Md & 1 in 1,000& For Swedish names&hehe\\
-		$\pi$ & 1 in 5& Common in math&hehe\\
-		\$ & 4 in 5 & Used in business&hehe\\
-		$\Psi^2_1$ & 1 in 40,000& Unexplained usage&hehe\\
+			We + Ws + Wa + Me + Wp + Wl + Wi + Pt + Md & 79.93\% & 57.45\% & 66.85\% \\
+
+			Ws + Wa + Me + Wp + Wl + Wi + Pt + Md & 84.01\% & 75.79\% & 79.69\% \\
+
+			We + Wa + Me + Wp + Wl + Wi + Pt + Md & 76.39\% & 73.59\% & 74.96\% \\
+
+			We + Ws + Me + Wp + Wl + Wi + Pt + Md & 78.44\% & 73.83\% & 76.07\% \\
+
+			We + Ws + Wa + Wp + Wl + Wi + Pt + Md & 79.38\% & 76.28\% & 77.8\% \\
+
+			We + Ws + Wa + Me + Wl + Wi + Pt + Md & 74.24\% & 78.23\% & 76.19\% \\
+
+			We + Ws + Wa + Me + Wp + Wi + Pt + Md & 75.36\% & 76.28\% & 75.82\% \\
+
+			We + Ws + Wa + Me + Wp + Wl + Pt + Md & 83.69\% & 75.3\% & 79.27\% \\
+
+			We + Ws + Wa + Me + Wp + Wl + Wi + Md & 79.68\% & 74.81\% & 77.17\% \\
+
+			We + Ws + Wa + Me + Wp + Wl + Wi + Pt & 75.66\% & 76.03\% & 75.85\% \\
 		\bottomrule
@@
 
-The experimental results in Table X shows that every feature has a positive contribution to the model.
-It is shown by iteratively remove each feature one by one and every time we remove a feature, F-1 score dropped.
+The experimental results in Table \ref{tab:ablation} shows that every feature has a positive contribution to the model.
+It is shown by iteratively remove each feature one by one and every time we remove a feature, F-1 score always dropped.
 Hence, we use every feature to train our model in the next experiments.
-Table X shows the performances of different methods.
+\subsection{Model Scenario}
+We created a scenario to evaluate the performance of our model.
+In this scenario, we also compared our model to an unsupervised learning algorithm using RAKE.
+Moreover, we also implemented CRF to as a baseline for this sequence labeling task.
+CRF also has been proven effective in extracting keyphrases \cite{cao2010automatically} \cite{zhang2008automatic}.
+The following scenarios are listed below:
+\begin{itemize}
+	\item RAKE
+	\item CRF
+	\item B-LSTM
+	\item CNN-B-LSTM
+	\item Weighting-CNN-B-LSTM
+\end{itemize}
+The result of the scenario can be seen in Table \ref{tab:model_scenario}.
+\begin{table}
+	\caption{Model Scenario Result}
+	\label{tab:model_scenario}
+	\begin{tabular}{lccc}
+		\toprule
+		Models&Precision&Recall&F-Measure\\
+		\midrule
+			RAKE & 43.24\% & 68.19\% & 52.90\% \\
+
+			CRF & 63.44\% & 64.94\% & 62.52\% \\
+
+			LSTM & 78.77\% & 79.71\% & 79.16\% \\
+
+			B-LSTM & 81.88\% & 83.05\% & 82.37\% \\
+
+			CNN-B-LSTM & 82.00\% & 82.99\% & 82.41\% \\
+
+		\bottomrule
+	\end{tabular}
+\end{table}
 \section{INI CONTOH}

### 2017-05-22 sig-alternate.tex
Updates from ShareLaTeX

@@
 
-Keyphrases are usually selected phrases or clauses that can capture the main topic of a given document \citep{turney2000learning}.
+Keyphrases are usually selected phrases or clauses that can capture the main topic of a given document \cite{turney2000learning}.
 They can provide readers with highly valuable and representative information, such that looking at keyphrases is sufficient to understand the whole body of document.
-Moreover, keyphrases are important for text summarization, document clustering, and classification task (\citep{classDocumentEkp1}; \citep{qaEkp}; \citep{gong2009improving}).
-Previous works have shown that using keyphrases to generate queries can improve the quality of question retrieval in medical question answering forum \citep{cao2010automatically}.
+Moreover, keyphrases are important for text summarization, document clustering, and classification task (\cite{classDocumentEkp1}; \cite{qaEkp}; \cite{gong2009improving}).
+Previous works have shown that using keyphrases to generate queries can improve the quality of question retrieval in medical question answering forum \cite{cao2010automatically}.
 
-Keyphrase extraction methods have been mostly using statistical approach (\cite{sparck1972statistical}, \citep{zhang2007comparative}, \citep{rake}, \cite{mihalcea2004textrank}) and supervised learning approach (\citep{witten1999kea}; \citep{medelyan2009human}; \citep{marujoMAUI}).
+Keyphrase extraction methods have been mostly using statistical approach (\cite{sparck1972statistical} \cite{zhang2007comparative} \cite{rake} \cite{mihalcea2004textrank}) and supervised learning approach (\cite{witten1999kea} \cite{medelyan2009human} \cite{marujoMAUI}).
 The statistical approach often involves keyword candidate selection and candidate's property calculation.
-The "keywordness" value of a candidate phrase is usually scored based on its typical length as well as frequency in which document it appears \citep{rake}.
+The "keywordness" value of a candidate phrase is usually scored based on its typical length as well as frequency in which document it appears \cite{rake}.
 While the statistical approach is very efficient to generate keyphrases, our experiments showed that it performs poorly on user generated contents and short documents.
 The other approach is based on supervised learning, there are two common approach in supervised learning: classification and sequence labeling.
-In classification approach, candidate keyphrases are extracted using statistical \citep{sparck1972statistical} or language model \citep{ekpNeuralNetworks}.
+In classification approach, candidate keyphrases are extracted using statistical \cite{sparck1972statistical} or language model \cite{ekpNeuralNetworks}.
 Then, the candidate keyphrases are classified whether a candidate is a keyphrase or not by using a pretrained model.
-However, classification approach cannot capture semantic relationship between words in a document \citep{surveyPopulerTerbaruEkp}.
-In sequence labeling approach,  like the one proposed by \citep{cao2010automatically} and \cite{zhang2008automatic}.
+However, classification approach cannot capture semantic relationship between words in a document \cite{surveyPopulerTerbaruEkp}.
+In sequence labeling approach,  like the one proposed by \cite{cao2010automatically} and \cite{zhang2008automatic}.
 They define keyphrase extraction task as a sequence labeling task, in which each word in the document can have two possible labels: keyword or non-keyword.
 The method they proposed worked well by outperforming unsupervised approach.
-However, synonym and ambiguity words cannot be handled properly \citep{zhang2008automatic}
+However, synonym and ambiguity words cannot be handled properly \cite{zhang2008automatic}.
 
@@
 After that, the dataset was used for both training and testing our computational models.
-For our baseline, we use RAKE  \citep{rake}, which is the current state of the art model for extracting keyphrases.
+For our baseline, we use RAKE  \cite{rake}, which is the current state of the art model for extracting keyphrases.
 
@@
 
-\section{The {\secit Body} of The Paper}
-Typically, the body of a paper is organized
-into a hierarchical structure, with numbered or unnumbered
-headings for sections, subsections, sub-subsections, and even
-smaller sections.  The command \texttt{{\char'134}section} that
-precedes this paragraph is part of such a
-hierarchy.\footnote{This is the second footnote.  It
-starts a series of three footnotes that add nothing
-informational, but just give an idea of how footnotes work
-and look. It is a wordy one, just so you see
-how a longish one plays out.} \LaTeX\ handles the numbering
-and placement of these headings for you, when you use
-the appropriate heading commands around the titles
-of the headings.  If you want a sub-subsection or
-smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both
-numbered and unnumbered headings will appear throughout the
-balance of this sample document.
+\section{Related Works}
+In general, keyphrase extraction methods can be divided into two groups: unsupervised ranking (statistical) approach and supervised machine learning approach.
+For the unsupervised line of research, keyphrase extraction is formulated as a ranking problem, in which each candidate keyphrase is assigned a score that represents its keywordness value.
+Furthermore, this kind of approach does not require training data, which is often very difficult to obtain.
+On the other hand, supervised machine learning approach requires training data that contains a collection of documents with their labeled keywords.
+Using this approach, keyphrase extraction is usually treated as a classification or sequence labeling task in the level of words or phrases.
+The first step of this approach generates candidate keyphrases from a particular document.
+Finally, every candidate keyphrase in the document will be classified as either a keyphrase or non-keyphrase.
+Recently, a well-known supervised approach for keyphrase extraction is based on sequence labeling problem (\cite{zhang2008automatic}\cite{cao2010automatically}\cite{zhang2016keyphrase}).
+The assumption behind this model is that the decision on whether a particular word serves as a keyword is affected by the information from its neighboring word positions.
 
-Because the entire article is contained in
-the \textbf{document} environment, you can indicate the
-start of a new paragraph with a blank line in your
-input file; that is why this sentence forms a separate paragraph.
+In the work of \cite{sparck1972statistical}, they leverage TF-IDF to get the most significant words.
+Specifically, they utilize term frequency and the inverse of document frequency to rank terms in the document.
+First, this Rapid Automatic Keywords Extraction \cite{rake} uses stopwords to split a document into several candidate keyphrases.
+All candidates will be ranked by the degrees and frequencies of all words inside them.
+Finally, the rank points of each candidate is obtained by summing over all degrees and frequencies of all words contained in each keyphrase.
+RAKE is proven to be successful for extracting keyphrases in special documents such as paper and article \cite{rake}.
 
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with
-the command \texttt{{\char'134}textit}; emboldening with the
-command \texttt{{\char'134}textbf}
-and typewriter-style (for instance, for computer code) with
-\texttt{{\char'134}texttt}.  But remember, you do not
-have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your
-article; for instance, the heading of this subsection will
-be in a sans serif\footnote{A third footnote, here.
-Let's make this a rather short one to
-see how it looks.} typeface, but that is handled by the
-document class file. Take care with the use
-of\footnote{A fourth, and last, footnote.}
-the curly braces in typeface changes; they mark
-the beginning and end of
-the text that is to be in the different typeface.
+There is also a popular graph-based approach, namely TextRank (U), i.e., a modified PageRank algorithm to extract keyphrases from a document.
+They exploit word co-occurrence information to build a document graph, in which a word serves as a node and co-occurence information determines an edge between two nodes (words).
+After they build the graph, they actually run PageRank algorithm to determine the keywordness score for each node in the graph.
+A word with high PageRank value denotes that its related concept can be found in many location inside the document, which means that it is a good candidate for keyword.
+After that, keyphrases can be obtained using post-processing step that may combine contiguous candidates into one keyphrase.
 
-You can use whatever symbols, accented characters, or
-non-English characters you need anywhere in your document;
-you can find a complete list of what is
-available in the \textit{\LaTeX\
-User's Guide}\cite{Lamport:LaTeX}.
+One of the earlier supervised approaches in the problem of keyphrase extraction is KEA \cite{witten1999kea}.
+KEA uses tf-idf and first occurrence of the term to identify candidate keyphrases.
+They use a machine-learning algorithm (i.e., Naive Bayes) to predict whether or not a candidate is a good keyphrase.
+\cite{medelyan2009human} developed a system called MAUI that can extract keyphrases using trained corpus and controlled vocabulary.
+MAUI itself is an improvement to the aforementioned supervised model, KEA.
+Furthermore, \cite{marujoMAUI} use word embedding and brown clustering as features.
+Their experiment result had shown that the proposed features and MAUI performs better than statistical methods, such as simple tf-idf approach.
 
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
+The utilization of neural networks is also quite popular in the recent years.
+\cite{ekpNeuralNetworks} uses Feed Forward Neural Networks to classify candidate keyphrases.
+To extract candidate keyphrases, they use POS tag information for classifying all words in the document.
+Then, Deterministic Finite Automation (DFA) is used to extract noun phrases as candidate keyphrases.
+Furthermore, deep neural networks is also employed for extracting keyphrase, like the one proposed by \cite{zhang2016keyphrase}, that uses joint Recurrent Neural Networks (RNNs) layer to capture keyphrase sequences in microblogs.
+The research had shown that RNN is very effective to extract keyword.
 
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-construction or with the short form \texttt{\$. . .\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space
-from the text and centered horizontally -- is produced
-by the \textbf{equation} environment. An unnumbered display
-equation is produced by the \textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning,
-clark:pct, braams:babel, herlihy:methodology},
-conference proceedings \cite{clark:pct} or
-books \cite{salas:calculus, Lamport:LaTeX} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file \cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
-
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
-
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed or supported.
-
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
-
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
-
-\begin{table*}
-\centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
-
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
-
-This sample document contains examples of \textbf{.eps}
-and \textbf{.ps} files to be displayable with \LaTeX.  More
-details on each of these is found in the \textit{Author's Guide}.
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps}
-\caption{A sample black and white graphic (.eps format).}
-\end{figure}
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps, height=1in, width=1in}
-\caption{A sample black and white graphic (.eps format)
-that has been resized with the \texttt{epsfig} command.}
-\end{figure}
-
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption.
-and don't forget to end the environment with
-{figure*}, not {figure}!
-
-\begin{figure*}
-\centering
-\epsfig{file=flies.eps}
-\caption{A sample black and white graphic (.eps format)
-that needs to span two columns of text.}
-\end{figure*}
-
-Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
-used; use
-the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
-commands as appropriate for the different file types.
-
-\begin{figure}
-\centering
-\psfig{file=rosette.ps, height=1in, width=1in,}
-\caption{A sample black and white graphic (.ps format) that has
-been resized with the \texttt{psfig} command.}
-\vskip -6pt
-\end{figure}
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
-
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
-
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
-
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to
-use the \texttt{{\char'134}newdef} command to create a
-new form, you might think you can
-use \TeX's \texttt{{\char'134}def} to create a
-new command: \textit{Please refrain from doing this!}
-Remember that your \LaTeX\ source code is primarily intended
-to create camera-ready copy, but may be converted
-to other forms -- e.g. HTML. If you inadvertently omit
-some or all of the \texttt{{\char'134}def}s recompilation will
-be, to say the least, problematic.
+Unfortunately, there are limited works regarding the task of keyphrase extraction in medical domain.
+\cite{ekpMedicalDocumentHybrid} use a hybrid medical knowledge base and statistical approach to extract keyphrases from medical articles.
+They use stopwords to split candidate keyphrases, then candidates are ranked with two aspects: PF-IDF (Phrase Frequency * Inverse Document Frequency) and domain knowledge which is extracted from medical article.
+In terms of medical social media content, \cite{cao2010automatically} use Conditional Random Fields (CRFs) for extracting keywords from medical questions in online health-forum.
+They use information, such as word location and length as features in their experiments.
 

### 2017-05-23 samplebody-conf.tex
add desc table
Add several formula

@@
 There is also a popular graph-based approach, namely TextRank (U), i.e., a modified PageRank algorithm to extract keyphrases from a document.
-They exploit word co-occurrence information to build a document graph, in which a word serves as a node and co-occurence information determines an edge between two nodes (words).
-After they build the graph, they actually run PageRank algorithm to determine the keywordness score for each node in the graph.
+They exploit word co-occurrence information to build a document graph, in which a word serves as a vertice and co-occurence information determines an edge between two vertices (words).
+After they build the graph, they actually run PageRank algorithm to determine the keywordness score for each vertice in the graph.
 A word with high PageRank value denotes that its related concept can be found in many location inside the document, which means that it is a good candidate for keyword.
@@
 There is also unnecessary information such as URL and email.
-We replace URL with “URL”  and email with “email” since we were focusing on textual content.
+We replace URL with "URL"  and email with "email" since we were focusing on textual content.
 Moreover, we also removed ads and spam in the data we gathered.
@@
 The statistical information of the dataset can be seen in Table X
+\begin{table}
+	\caption{Statistical information of dataset.
+W, K, $\bar{N}_{w}$, $\bar{N}_{k}$ are the total of words, number of keyphrases, average number of words, and average number of keyphrases in each question, respectively.}
+	\label{tab:descriptive_stats}
+	\begin{tabular}{lcccc}
+		\toprule
+		\#questions&W&K&$\bar{N}_{w}$&$\bar{N}_{k}$\\
+		\midrule
+		416 & 26747  & 64.76 & 1861 & 4.49 \\
 
+		\bottomrule
+	\end{tabular}
+\end{table}
 \subsection{TASK DEFINITIONS}
+
+\subsection{FEATURES}
+Because the small dataset that we have, our model would have a small learning material and an end-to-end approach might not work well.
+As a result, We leveraged nine handcrafted features that help the model in learning.
+\subsubsection{Word embedding\\}
+In the experiments, we use word embedding as input to the neural network.
+A skip-gram model \cite{mikolov2013wordembed} was used to generate these 128-dimensional vectors for documents in evaluation data.
+The dimension of the vector were chosen based on \cite{skripsiWahid} experiment.
+The word embeddings we used in this work were trained using a document that we gathered from Indonesia online forum, medical article, and medical question answering forum.
+
+\subsubsection{Medical Dictionary\\}
+In our experiment, we leveraged a medical knowledge base feature using a medical dictionary.
+Our medical dictionary contains a list of symptom, disease, treatment, and drug in the Indonesian language.
+The rationale behind this feature is intentions and needs of patients is more focused on their disease, symptom, treatment, and drug.
+Based on this feature, we classified words by their appearance in the medical dictionary.
+The dictionary was built by combining three dictionaries from \cite{skripsiKakAbid} research.
+The original dictionaries contained disease, symptom, treatment, and drug separately in each dictionary.
+
+\subsubsection{Word Length\\}
+This feature represents the length of each word (i.e., the number of characters in every word).
+This feature is based on \cite{cao2010automatically} research on keyphrase extraction in medical question who added word length as a feature because domain-specific words (e.g.
+"tuberculosis") tend to be lengthy when compared to common English words, and there is a correlation between the length of a word and its IDF value \citep{cao2010automatically}.
+Thus we use the same feature for Indonesian language.
+
+\subsubsection{Word Position\\}
+We also adapted word position as feature based on \cite{cao2010automatically}research.
+Based on their observation, an important term sometimes appears toward the end of a clinical question.
+For example, "medicine for bell’s palsy" appear towards the end of question "what is the best medicine for bell’s palsy?".
+
+\subsubsection{POS-tag\\}
+POS-tag of words was also added as our feature.
+POS-tag may give model grammatical information and a better understanding of ambiguous words.
+By our observation, many keyphrases have a common POS pattern.
+For example, "treatment\_Noun for\_Preposition cancer\_Noun", "therapy\_Noun for\_Preposition headache\_Noun".
+Moreover, \cite{skripsiWahid}, and \cite{abacha2011medical} have proven that POS tag feature has a positive contribution in sequence labeling task in Indonesian medical domain such as Medical Entities Recognizer (MER).
+
+\subsubsection{Medical Entity\\}
+We use medical entity which annotated by \cite{skripsiWahid}.
+By our observation, medical entities are sometimes part of keyphrases.
+Furthermore, medical entities can provide more information about drug or disease which not available in training data or a medical dictionary.
+
+\subsubsection{Abbreviation and Acronym\\}
+We also identified words by their appearance in abbreviation or acronym dictionary gathered by \cite{skripsiKakAbid}.
+We observed that important word may not be shortened by the users, such as "cancer", "flu", "bell’s palsy".
+
+\subsubsection{Word Importance\\}
+We also leveraged a word importance feature.
+The purpose of this feature is to rank words in a document by their importance.
+The "keywordness" value of a word can be determined by the importance value.
+To extract this feature, we adapted a method from TextRank \cite{mihalcea2004textrank} algorithm for ranking words in a document.
+They represent words as vertices in graph and the distance between words as edges.
+However, in building an undirected graph, we use a word similarity by using our trained word embedding model.
+Two words have a connected edge, if their similarity is not negative.
+The weight of the edge is the similarity itself.
+Moreover, we use a modified PageRank \cite{page1999pagerank} algorithm that consider edges weight in the calculation.
+Formally, let $G = (V, E)$ be an undirected graph with the set of vertices V and set of edges E, where E is a subset of $VxV$.
+For a given vertex $V_i$ let $In(V_i)$ be the set of vertices that point to it (predecessors), and let $Out(V_i)$ be the set of vertices that vertex $V_i$ points to (successors).
+The modified PageRank formula that proposed by \cite{mihalcea2004textrank} can be seen in Formula \ref{eq:pagerank}.
+\begin{equation}\label{eq:pagerank}
+	WS(V_{i})=(1-d) + d * \sum_{V_{i} \in In(V_{i})} \frac{w_{ji}}{\sum_{V_{i} \in Out(V_{j})}}w_{jk}
+\end{equation}
+
+\subsubsection{Word Stickiness\\}
+As a keyphrase, a sequence must be in a valid order.
+There is some noise such as misuse punctuation by users.
+For example, "Saya mengalami pusing pada jidat sakit perut dan pandangan kabur (I am having a headache on forehead stomachache and blurred vision)", there is no comma between "jidat (forehead)", "sakit perut (stomachache)" and "dan (and)".
+Our model may mistake the sequence "(jidat sakit perut)forehead stomachache" as a keyphrase.
+Based on that problem, we propose a feature that may capture how likely of a given word is occurred together with the word before and after.
+We use Pointwise Mutual Information (PMI) of a bigram probability to capture the likeness.
+This feature represented as two dimensional vector $v = [x1, x2]$, with $x_1$ is the PMI with the word before and $x_2$ is the PMI with the word after.
+Formula \ref{eq:pmi} is the formula for calculating the PMI value.
+In that formula, $p(x)$ is the occurrence probability of word $x$, $p(y)$ is the occurrence probability of word $y$, and $p(x, y)$ is the probability of word $x$ and $y$ co-occur together.
+\begin{equation}\label{eq:pmi}
+	PMI(x,y)=log(\frac{p(x, y)}{p(x)*p(y)})
+\end{equation} 
 \subsection{MODEL ARCHITECTURE}
@@
 From our observation, to know whether a word is part of keyphrase or not, we need to know the context of the word itself.
-For example, “Doc, i have a frequent back pain.
-What happen?”.
-The keyphrase for previous example is “frequent back pain”.
-In order to know that “back” is part of keyphrase, we need information from the word “frequent” which give an intensity of a symptom and “pain” which refer to “back pain” as main term.
+For example, "Doc, i have a frequent back pain.
+What happen?".
+The keyphrase for previous example is "frequent back pain".
+In order to know that "back" is part of keyphrase, we need information from the word "frequent" which give an intensity of a symptom and "pain" which refer to "back pain" as main term.
 With CNNs, we argue that our model can capture the surrounding information of a word.
@@
 Hence, we utilized  bi-directional LSTM (B-LSTM) for extracting structural knowledge by processing sequences both forward and backward.
+We build up to two layers of B-LSTM.
 To perform the sequence tagging task, we build a fully connected layer in the top of our model. This layer will classify the output of our model with softmax activation function.
@@
 In this section, we analyzed the importance of our features by conducting a feature ablation study. Furthermore, we also established a scenario to test the performance of our model.
+\subsection{Evaluation}
+One of the evaluation that we use in our work is using partial evaluation.
+This evaluation is used because we treat keyphrases as sequences of words.
+Thus we can use partial evaluation which is used to evaluate Named Entity Recognition system.
+In partial evaluation method, a assigned keyphrase is predicted correctly if a predicted keyphrase has a word which is a subset in assigned keyphrase words.
+
+We use Recall, Precision, and F1 score as our evaluation parameters.
+Recall shows the number of correctly predicted keyphrases divided by the the total number of assigned keyphrases and Precision is the number of correctly predicted keyphrase divided by the total number of predicted keyphrases.
+To calculate F1 score we use Recall and Precision as parameters which is 2  Recall  Precision/ (Recall + Precision).
 \subsection{Feature Ablation Study}
@@
 		\midrule
-			We + Ws + Wa + Me + Wp + Wl + Wi + Pt + Md & 79.93\% & 57.45\% & 66.85\% \\
+		We + Ws + Wa + Me + Wp + Wl + Wi + Pt + Md & \textbf{84.01\%} & 75.79\% & \textbf{79.69\%} \\
 
-			Ws + Wa + Me + Wp + Wl + Wi + Pt + Md & 84.01\% & 75.79\% & 79.69\% \\
+		Ws + Wa + Me + Wp + Wl + Wi + Pt + Md & 79.93\% & 57.45\% & 66.85\% \\
 
@@
 
-			We + Ws + Wa + Me + Wl + Wi + Pt + Md & 74.24\% & 78.23\% & 76.19\% \\
+		We + Ws + Wa + Me + Wl + Wi + Pt + Md & 74.24\% & \textbf{78.23\%} & 76.19\% \\
 
@@
 
-			B-LSTM & 81.88\% & 83.05\% & 82.37\% \\
+		B-LSTM & 81.88\% & \textbf{83.05\%} & 82.37\% \\
 
-			CNN-B-LSTM & 82.00\% & 82.99\% & 82.41\% \\
+		CNN-B-LSTM & \textbf{82.00\%} & 82.99\% & \textbf{82.41\%} \\
 
@@
 \end{table}
-\section{INI CONTOH}
-\subsection{Type Changes and {\itshape Special} Characters}
+Table \ref{tab:model_scenario} shows the performance of different methods that we proposed on dataset we have.
+To evaluate or model we use 10-cross fold validation.
+From the results, we observed that every supervised method using sequence labeling approach achieved a better performance than RAKE.
+The best result achieved by CNN with two stacked B-LSTM with 82.41\% F-Score.
+RAKE Perform the worst.
+The result shows that RAKE only achieved 52.9\% F-Score.
+This is because RAKE using statistical approach to weight candidate keyphrases which becoe a problem in short document like medical questions.
+Furthermore, RAKE using stopwords to split candidate keyphrases in document, but user-generated content tend to have a bad structural information.
+Thus there are some misplaced stopwords in the content.
+Among other methods, CRF performed the worst.
+Bidirectional approach shows effectiveness because B-LSTM has a better result than LSTM.
+Furthermore, using CNN to capture context between words also shows improvement and it become the best result in our experiment.
+However, when we use CRF on the top of our model the results dropped.
+The experiment results indicated our context aware CNN and B-LSTM worked well in keyphrase extraction in Indonesian user-generated medical domain.
 
-We have already seen several typeface changes in this sample.  You can
-indicate italicized words or phrases in your text with the command
-\texttt{{\char'134}textit}; emboldening with the command
-\texttt{{\char'134}textbf} and typewriter-style (for instance, for
-computer code) with \texttt{{\char'134}texttt}.  But remember, you do
-not have to indicate typestyle changes when such changes are part of
-the \textit{structural} elements of your article; for instance, the
-heading of this subsection will be in a sans serif\footnote{Another
-  footnote here.  Let's make this a rather long one to see how it
-  looks.} typeface, but that is handled by the document class file.
-Take care with the use of\footnote{Another footnote.}  the
-curly braces in typeface changes; they mark the beginning and end of
-the text that is to be in the different typeface.
+We also tried our feature weighting layer in our best model which is CNN with B-LSTM and fully-connected hidden layer on top.
+The result in Table \ref{tab:weighting_scenario} shows that our weighting layer not worked quite well.
+We suspect the gap of information between features are on of the reason which cause the result drop
+\begin{table}
+	\caption{Weighting Layer Scenario Result}
+	\label{tab:weighting_scenario}
+	\begin{tabular}{lccc}
+		\toprule
+		Models&Precision&Recall&F-Measure\\
+		\midrule
+		CNN-B-LSTM & 82.00\% & 82.99\% & 82.41\% \\
 
-You can use whatever symbols, accented characters, or non-English
-characters you need anywhere in your document; you can find a complete
-list of what is available in the \textit{\LaTeX\ User's Guide}
-\cite{Lamport:LaTeX}.
-
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
-
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin\,\ldots{\char'134}end}
-construction or with the short form \texttt{\$\,\ldots\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsubsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX\@; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\subsection{Citations}
-Citations to articles~\cite{bowman:reasoning,
-clark:pct, braams:babel, herlihy:methodology},
-conference proceedings~\cite{clark:pct} or maybe
-books \cite{Lamport:LaTeX, salas:calculus} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file~\cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
-
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide} by Lamport~\shortcite{Lamport:LaTeX}.
-
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-are found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed
-output of this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
+		W-CNN-B-LSTM & 81.08\% & 81.18\% & 81.01\% \\
 		\bottomrule
@@
 \end{table}
+\subsection{Error Analysis}
+We performed an error analysis to the aforementioned model, the result shown there are several errors.
+Some of the error are uncompleted keyphrases.
+For example "headache on (sakit kepala pada)", "medicine for (obat untuk)".
+Our model also failed to capture complex medicine name and disease.
+This is due to our small data set and not all medicine and disease are captured in our knowledge base.
+Moreover, there are also special case for keyphrases like "treatment for headache and sore throat (penyembuhan untuk sakit kepala dan tenggorokan)", that keyphrase need to be captured as whole because "sore throat" have a connection with the word "treatment".
+But our model, failed to capture that connection, it extracted "treatment for headache" and "sore throat" separately.
+\section{Conclusion}
+We investigate a keyphrase extraction problem especially in Indonesian medical questions domain with sequence labeling approach.
+We leverage a deep learning approach using CNN and B-LSTM.
+Moreover, we also extracted nine features that capture medical concepts from a knowledge base, and linguistic components as our features.
+With this model and features, we are able to overcome problems such as informal language, short document, and medical domain specific.
+Our model achieves F1 score of 82.41\% on manually annotated Indonesian medical questions.
 
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
+For handling several problems that occurred in this experiment, we suggest to create a language model for post-processing.
+The language model expected to handle cases like uncompleted keyphrase or connection between keyphrase.
 
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
-
-It is strongly recommended to use the package booktabs~\cite{Fear05}
-and follow its main principles of typography with respect to tables:
-\begin{enumerate}
-\item Never, ever use vertical rules.
-\item Never use double rules.
-\end{enumerate}
-It is also a good idea not to overuse horizontal rules.
-
-\subsection{Figures}
-
-Like tables, figures cannot be split across pages; the best placement
-for them is typically the top or the bottom of the page nearest their
-initial cite.  To ensure this proper ``floating'' placement of
-figures, use the environment \textbf{figure} to enclose the figure and
-its caption.
-
-This sample document contains examples of \texttt{.eps} files to be
-displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
-\texttt{.pdf} format.  Note that most modern \TeX\ systems will convert
-\texttt{.eps} to \texttt{.pdf} for you on the fly.  More details on
-each of these are found in the \textit{Author's Guide}.
-
-\begin{figure}
-\includegraphics{fly}
-\caption{A sample black and white graphic.}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=1in, width=1in]{fly}
-\caption{A sample black and white graphic
-that has been resized with the \texttt{includegraphics} command.}
-\end{figure}
-
-As was the case with tables, you may want a figure that spans two
-columns.  To do this, and still to ensure proper ``floating''
-placement of tables, use the environment \textbf{figure*} to enclose
-the figure and its caption.  And don't forget to end the environment
-with \textbf{figure*}, not \textbf{figure}!
-
-\begin{figure*}
-\includegraphics{flies}
-\caption{A sample black and white graphic
-that needs to span two columns of text.}
-\end{figure*}
-
-\begin{figure}
-\includegraphics[height=1in, width=1in]{rosette}
-\caption{A sample black and white graphic that has
-been resized with the \texttt{includegraphics} command.}
-\end{figure}
-
-\subsection{Theorem-like Constructs}
-
-Other common constructs that may occur in your article are the forms
-for logical constructs like theorems, axioms, corollaries and proofs.
-ACM uses two types of these constructs:  theorem-like and
-definition-like.
-
-Here is a theorem:
-\begin{theorem}
-  Let $f$ be continuous on $[a,b]$.  If $G$ is
-  an antiderivative for $f$ on $[a,b]$, then
-  \begin{displaymath}
-    \int^b_af(t)\,dt = G(b) - G(a).
-  \end{displaymath}
-\end{theorem}
-
-Here is a definition:
-\begin{definition}
-  If $z$ is irrational, then by $e^z$ we mean the
-  unique number that has
-  logarithm $z$:
-  \begin{displaymath}
-    \log e^z = z.
-  \end{displaymath}
-\end{definition}
-
-The pre-defined theorem-like constructs are \textbf{theorem},
-\textbf{conjecture}, \textbf{proposition}, \textbf{lemma} and
-\textbf{corollary}.  The pre-defined de\-fi\-ni\-ti\-on-like constructs are
-\textbf{example} and \textbf{definition}.  You can add your own
-constructs using the \textsl{amsthm} interface~\cite{Amsthm15}.  The
-styles used in the \verb|\theoremstyle| command are \textbf{acmplain}
-and \textbf{acmdefinition}.
-
-Another construct is \textbf{proof}, for example,
-
-\begin{proof}
-  Suppose on the contrary there exists a real number $L$ such that
-  \begin{displaymath}
-    \lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-  \end{displaymath}
-  Then
-  \begin{displaymath}
-    l=\lim_{x\rightarrow c} f(x)
-    = \lim_{x\rightarrow c}
-    \left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-    = \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-    \frac{f(x)}{g(x)} = 0\cdot L = 0,
-  \end{displaymath}
-  which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-\section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
-%\end{document}  % This is where a 'short' article might terminate
-
-\appendix
-%Appendix A
-\section{Headings in Appendices}
-The rules about hierarchical headings discussed above for
-the body of the article are different in the appendices.
-In the \textbf{appendix} environment, the command
-\textbf{section} is used to
-indicate the start of each Appendix, with alphabetic order
-designation (i.e., the first is A, the second B, etc.) and
-a title (if you include one).  So, if you need
-hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this
-document in Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{References}
-Generated by bibtex from your \texttt{.bib} file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the \texttt{.bbl} file.  Insert that \texttt{.bbl}
-file into the \texttt{.tex} source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-% This next section command marks the start of
-% Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-
-Of course, reading the source code is always useful.  The file
-\path{acmart.pdf} contains both the user guide and the commented
-code.
-
-\begin{acks}
-  The authors would like to thank Dr. Yuhua Li for providing the
-  matlab code of  the \textit{BEPS} method.
-
-  The authors would also like to thank the anonymous referees for
-  their valuable comments and helpful suggestions. The work is
-  supported by the \grantsponsor{GS501100001809}{National Natural
-    Science Foundation of
-    China}{http://dx.doi.org/10.13039/501100001809} under Grant
-  No.:~\grantnum{GS501100001809}{61273304}
-  and~\grantnum[http://www.nnsf.cn/youngscientsts]{GS501100001809}{Young
-    Scientsts' Support Program}.
-
-\end{acks}
+Furthermore, we realized that there are no solid evaluation method for keyphrase extraction.
+Partial evaluation may handle how the model extract sequences in a document.
+However, weights for importance in sequences are different between words.
+For example "therapy for pregnancy", in that keyphrase we may realize that "pregnancy" is more important than other words.
+Thus partial evaluation failed to capture that problem.

### 2017-05-23 samplebody-conf.tex

@@
 However, synonym and ambiguity words cannot be handled properly \cite{zhang2008automatic}.
+For example, we give a medical question asked by a patient in Indonesian language:
+\begin{itemize}
+    \item 
+		Dok , saya sering sekali merasa \textbf{kram pada perut kanan bagian atas} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}.
+Dan saat kambuh seperti itu, \textbf{nafas sangat sakit}.
+Seminggu yang lalu sampai terkapar karena tidak kuat menahan sakitnya saat bernafas.
+bagaimana penanggulangannya saat kambuh?
+terima kasih sblumnya dok.
+\\\\
+		(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}.
+And when the symptom occur it's \textbf{very hurt when breathing}.
+Last week i fainted because cannot hold the pain when i was breathing.
+How is the treatment when it's occur?
+thanks before \\
+\end{itemize}
+It can be seen that keyphrases can be a word, phrase, or even clause. Furthermore, there are many grammatical error in the document that make the extraction process not trivial.
 
@@
 
-There is also a popular graph-based approach, namely TextRank (U), i.e., a modified PageRank algorithm to extract keyphrases from a document.
-They exploit word co-occurrence information to build a document graph, in which a word serves as a vertice and co-occurence information determines an edge between two vertices (words).
-After they build the graph, they actually run PageRank algorithm to determine the keywordness score for each vertice in the graph.
+There is also a popular graph-based approach, namely TextRank \cite{mihalcea2004textrank}, i.e., a modified PageRank algorithm to extract keyphrases from a document.
+They exploit word co-occurrence information to build a document graph, in which a word serves as a node and co-occurence information determines an edge between two nodes (words).
+After they build the graph, they actually run PageRank algorithm to determine the keywordness score for each node in the graph.
 A word with high PageRank value denotes that its related concept can be found in many location inside the document, which means that it is a good candidate for keyword.
@@
 \section{METHODOLOGY}
+In this work, we view our problem as a sequence labeling task.
+That is, given a medical question containing $N$ words $w = (w_1, w_2,...,w_N$, we want to find the best sequence pf labels $y = (y_1, y_2,..., y_N)$, in which each label is determined using probabilities $P(y_i|w_{i-l},...,w_{i+l},y_{i-l},...,y_{i+l})$ where $l$ is a small number.
+
 \subsection{DATA AND ANNOTATION}
@@
 In Table X, we give an example sequence with labels for each word.
-The statistical information of the dataset can be seen in Table X
+The statistical information of the dataset can be seen in Table \ref{tab:descriptive_stats}.
 \begin{table}
@@
 Based on their observation, an important term sometimes appears toward the end of a clinical question.
-For example, "medicine for bell’s palsy" appear towards the end of question "what is the best medicine for bell’s palsy?".
+For example, "medicine for bell's palsy" appear towards the end of question "what is the best medicine for bell's palsy?".
 
@@
 They represent words as vertices in graph and the distance between words as edges.
-However, in building an undirected graph, we use a word similarity by using our trained word embedding model.
+However, in building an indirect graph, we use a word similarity by using our trained word embedding model.
 Two words have a connected edge, if their similarity is not negative.
@@
 \end{table}
-Table \ref{tab:model_scenario} shows the performance of different methods that we proposed on dataset we have.
+Table \ref{tab:model_scenario} shows the performance of different methods that we proposed on the dataset we have.
 To evaluate or model we use 10-cross fold validation.
@@
 The result shows that RAKE only achieved 52.9\% F-Score.
-This is because RAKE using statistical approach to weight candidate keyphrases which becoe a problem in short document like medical questions.
+This is because RAKE using statistical approach to weight candidate keyphrases which become a problem in short document like medical questions.
 Furthermore, RAKE using stopwords to split candidate keyphrases in document, but user-generated content tend to have a bad structural information.

### 2017-05-23 samplebody-conf.tex
Cut introduction

@@
 There are tremendous amount of user-generated contents about medical information through the internet.
-As a result, there is a growing need for enriching medical-related knowledge, for which it can be very valuable for several tasks, such as medical document retrieval, medical question answering, and health-related text mining applications.
-However, understanding those various health-related contents, especially from social media, is simply not a trivial task since they are written in free text format (i.e.
+As a result, there is a growing need for enriching medical-related knowledge, for which it can be very valuable for several tasks, such as medical document retrieval, medical question answering, and health-related text mining applications \cite{cao2010automatically}.
+However, understanding those various health-related contents, especially from online forum, is simply not a trivial task since they are written in free text format (i.e.
 unstructured format), and often prone to grammatical and typographical glitches.
@@
 However, we argue that there are many missing pieces of information when we merely rely on medical entities or terminologies as our main information for representing a particular document.
-In this paper, we present new keyphrases extraction techniques to extract more important information about the concept expressed inside the document.
-Furthermore, we also propose a new definition of keyphrases, which is based on our observation of health-related documents.
+Hence, we leverage keyphrase to cover more valuable information.
+Keyphrases are usually selected phrases or clauses that can capture the main topic of a given document \cite{turney2000learning}.
+They can provide readers with highly valuable and representative information, such that looking at keyphrases is sufficient to understand the whole body of document.
+
+In this paper, we only focus the task of keyphrase extraction on Indonesian medical questions in online forum ,such as alodokter, health detik, doktergratis, dokter.id, doktersehat, klikdokter \footnote{www.alodokter.com, health.detik.com, www.dokter.id, www.doktersehat.com, www.klikdokter.com}.
+We present new keyphrases extraction techniques to extract more important information about the patient intentions and needs, which expressed inside Indonesian medical questions.
+Furthermore, we also propose a new definition of keyphrases, which is based on our observation of health-related and user-generated document.
 Actually, our final goal is to develop medical question answering systems to assist physicians or people obtaining health information.
-The work presented in this paper is absolutely inline with our goal, since important keyphrases of a question document can be used to formulate a query for the passage retrieval subsystem.
+The work presented in this paper is absolutely inline with our goal, since important keyphrases of a question document can be used to formulate a query for the passage retrieval subsystem \cite{gong2009improving}.
+The example of keyphrase extraction in medical document can be seen below:
 
+	Dok , saya sering sekali merasa \textbf{kram pada perut kanan bagian atas} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}.
+Dan saat kambuh seperti itu, \textbf{nafas sangat sakit}.
+Seminggu yang lalu sampai terkapar karena tidak kuat menahan sakitnya saat bernafas.
+bagaimana penanggulangannya saat kambuh?
+terima kasih sblumnya dok.
+\\\\
+	(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}.
+And when the symptom occur it's \textbf{very hurt when breathing}.
+Last week i fainted because cannot hold the pain when i was breathing.
+How is the treatment when it's occur?
+thanks before \\
+
+In our work, we use the same approach as \cite{cao2010automatically}, which treats keyphrase extraction as a sequence labeling task.
+In our experiment, we employed and combined various deep learning architectures, such as convolutional neural networks and bi-directional long short-term memory networks, to exploit high level features between neighboring word positions.
+To improve the quality of our model, we leverage several new hand-crafted features that can handle our keyphrase extraction problems in medical user-generated content, such as word importance and word stickiness features.
+The word importance feature is enable to rank words in a document by their importance value.
+The more important a word is to the content of document, the higher its "keywordness" value would seem to be.
+In addition, we also propose word stickiness feature to make our model constructs keyphrases better.
+%===========
+
+\iffalse
 Keyphrases are usually selected phrases or clauses that can capture the main topic of a given document \cite{turney2000learning}.
@@
 In classification approach, candidate keyphrases are extracted using statistical \cite{sparck1972statistical} or language model \cite{ekpNeuralNetworks}.
-Then, the candidate keyphrases are classified whether a candidate is a keyphrase or not by using a pretrained model.
+Then, the candidate keyphrases are classified whether a candidate is a keyphrase or not by using a pre-trained model.
 However, classification approach cannot capture semantic relationship between words in a document \cite{surveyPopulerTerbaruEkp}.
@@
 
-In our work, we use the same approach as \cite{cao2010automatically} which treats keyphrase extraction as a sequence labeling task.
+In our work, we use the same approach as Cao \cite{cao2010automatically} which treats keyphrase extraction as a sequence labeling task.
 In our experiment, we employed and combined various deep learning architectures, such as convolutional neural networks and bi-directional long short-term memory networks, to exploit high level features between neighboring word positions.
@@
 We present the evaluation and the experimental results in section 4.
-
+\fi
 \section{Related Works}

### 2017-05-23 samplebody-conf.tex
Huge truncation in introduction, related work, and data collection

@@
 
+It can be seen on the example that keyphrases can be a word, phrase, or even clause.
+Furthermore, there are many grammatical error in user-generated document that make the extraction process not trivial.
+
 In our work, we use the same approach as \cite{cao2010automatically}, which treats keyphrase extraction as a sequence labeling task.
@@
 In addition, we also propose word stickiness feature to make our model constructs keyphrases better.
-%===========
+%===========Unused Introduction========================
 
@@
 How is the treatment when it's occur?
-thanks before \\
+thanks before) \\
 \end{itemize}
@@
 \fi
+%====================================================
 \section{Related Works}
+In general, keyphrase extraction methods can be divided into two groups: unsupervised ranking (statistical) approach and supervised machine learning approach.
+For the unsupervised line of research, keyphrase extraction is formulated as a ranking problem, in which each candidate keyphrase is assigned a score that represents its keywordness value.
+The well known researches in unsupervised approach are \cite{rake} which use the ratio of word degree and frequency to rank terms.
+\cite{mihalcea2004textrank} developed a graph based approach which treats words as vertices and construct edges between words using co-occurrence.
+
+Furthermore, this kind of approach does not require training data, which is often very difficult to obtain.
+On the other hand, supervised machine learning approach requires training data that contains a collection of documents with their labeled keywords.
+Using this approach, keyphrase extraction is usually treated as a classification or sequence labeling task in the level of words or phrases.
+The first step of this approach generates candidate keyphrases from a particular document.
+Finally, every candidate keyphrase in the document will be classified as either a keyphrase or non-keyphrase.
+The well known method for this approach is KEA \cite{witten1999kea}, they use machine-learning (i.e., Naive Bayes)for classifying candidate keyphrases.
+The utilization of neural networks in classifying candidate keyphrases also conducted by \cite{ekpNeuralNetworks}.
+Recently, a well-known supervised approach for keyphrase extraction is based on sequence labeling problem (\cite{zhang2008automatic}, \cite{cao2010automatically}, \cite{zhang2016keyphrase}).
+The assumption behind this model is that the decision on whether a particular word serves as a keyword is affected by the information from its neighboring word positions.
+
+Unfortunately, there are limited works regarding the task of keyphrase extraction in medical domain.
+\cite{ekpMedicalDocumentHybrid} use a hybrid medical knowledge base and statistical approach to extract keyphrases from medical articles.
+They use stopwords to split candidate keyphrases, then candidates are ranked with two aspects: PF-IDF (Phrase Frequency * Inverse Document Frequency) and domain knowledge which is extracted from medical article.
+In terms of medical social media content, \cite{cao2010automatically} use Conditional Random Fields (CRFs) for extracting keywords from medical questions in online health-forum.
+They use information, such as word location and length as features in their experiments.
+
+%=============================Unused Related Works=======
+\iffalse
 In general, keyphrase extraction methods can be divided into two groups: unsupervised ranking (statistical) approach and supervised machine learning approach.
@@
 They use information, such as word location and length as features in their experiments.
+\fi
+%===============================================
+\section{METHODOLOGY}
 
-\section{METHODOLOGY}
-In this work, we view our problem as a sequence labeling task.
-That is, given a medical question containing $N$ words $w = (w_1, w_2,...,w_N$, we want to find the best sequence pf labels $y = (y_1, y_2,..., y_N)$, in which each label is determined using probabilities $P(y_i|w_{i-l},...,w_{i+l},y_{i-l},...,y_{i+l})$ where $l$ is a small number.
-
+\iffalse
 \subsection{DATA AND ANNOTATION}
@@
 \end{table}
-\subsection{TASK DEFINITIONS}
+\fi
 
+\subsection{Problem Definitions}
+In this work, we view our problem as a sequence labeling task.
+That is, given a medical question containing $N$ words $w = (w_1, w_2,...,w_N$, we want to find the best sequence pf labels $y = (y_1, y_2,..., y_N)$, in which each label is determined using probabilities \\$P(y_i|w_{i-l},...,w_{i+l},y_{i-l},...,y_{i+l})$ \\where $l$ is a small number.
 \subsection{FEATURES}
@@
 As a result, We leveraged nine handcrafted features that help the model in learning.
-\subsubsection{Word embedding\\}
-In the experiments, we use word embedding as input to the neural network.
+\begin{enumerate}
+    \item \textit{Word Embedding.} In the experiments, we use word embedding as input to the neural network.
 A skip-gram model \cite{mikolov2013wordembed} was used to generate these 128-dimensional vectors for documents in evaluation data.
@@
 
-\subsubsection{Medical Dictionary\\}
-In our experiment, we leveraged a medical knowledge base feature using a medical dictionary.
+    \item \textit{Medical Dictionary.} In our experiment, we leveraged a medical knowledge base feature using a medical dictionary.
 Our medical dictionary contains a list of symptom, disease, treatment, and drug in the Indonesian language.
@@
 
-\subsubsection{Word Length\\}
-This feature represents the length of each word (i.e., the number of characters in every word).
+    \item \textit{Word Length.} This feature represents the length of each word (i.e., the number of characters in every word).
 This feature is based on \cite{cao2010automatically} research on keyphrase extraction in medical question who added word length as a feature because domain-specific words (e.g.
@@
 
-\subsubsection{Word Position\\}
-We also adapted word position as feature based on \cite{cao2010automatically}research.
+    \item \textit{Word Postion.} We also adapted word position as feature based on \cite{cao2010automatically}research.
 Based on their observation, an important term sometimes appears toward the end of a clinical question.
@@
 
-\subsubsection{POS-tag\\}
-POS-tag of words was also added as our feature.
+    \item \textit{POS-tag.} POS-tag of words was also added as our feature.
 POS-tag may give model grammatical information and a better understanding of ambiguous words.
@@
 
-\subsubsection{Medical Entity\\}
-We use medical entity which annotated by \cite{skripsiWahid}.
+    \item \textit{Medical Entity.} We use medical entity which annotated by \cite{skripsiWahid}.
 By our observation, medical entities are sometimes part of keyphrases.
@@
 
-\subsubsection{Abbreviation and Acronym\\}
-We also identified words by their appearance in abbreviation or acronym dictionary gathered by \cite{skripsiKakAbid}.
+    \item \textit{Abbreviation and Acronym.} We also identified words by their appearance in abbreviation or acronym dictionary gathered by \cite{skripsiKakAbid}.
 We observed that important word may not be shortened by the users, such as "cancer", "flu", "bell’s palsy".
 
-\subsubsection{Word Importance\\}
+    \item Word Importance.
 We also leveraged a word importance feature.
@@
         \end{equation}
-
-\subsubsection{Word Stickiness\\}
+    \item Word Stickiness.
 As a keyphrase, a sequence must be in a valid order.
@@
     \end{equation}
+\end{enumerate}
 \subsection{MODEL ARCHITECTURE}
@@
 Where $W_{i}$ are the weight for each feature and $F_{i}$ are the extracted feature in vector form.
-\section{EXPERIMENTS}
-In this section, we analyzed the importance of our features by conducting a feature ablation study. Furthermore, we also established a scenario to test the performance of our model.
+
+\section{Evaluations and Results}
+\subsection{Data Collection}
+To develop training data, we collected question-answer pairs which previously crawled by Abid \cite{skripsiKakAbid} and Wahid \cite{skripsiWahid} from Indonesian question-answering medical forum.
+Then, we selected 416 distinct question-answer pairs and removed the answer section for every pair because it's not relevant for obtaining patient intentions and needs.
+Finally, we manually annotated those questions.
+The statistical information of our data can be seen in Table \ref{tab:descriptive_stats}
+
+\begin{table}
+	\caption{Statistical information of dataset.
+W, K, $\bar{N}_{w}$, $\bar{N}_{k}$ are the total of words, number of keyphrases, average number of words, and average number of keyphrases in each question, respectively.}
+	\label{tab:descriptive_stats}
+	\begin{tabular}{lcccc}
+		\toprule
+		\#questions&W&K&$\bar{N}_{w}$&$\bar{N}_{k}$\\
+		\midrule
+		416 & 26747  & 64.76 & 1861 & 4.49 \\
+
+		\bottomrule
+	\end{tabular}
+\end{table}
 \subsection{Evaluation}
@@
 To calculate F1 score we use Recall and Precision as parameters which is 2  Recall  Precision/ (Recall + Precision).
+%===========Commented Feature Ablation Study
+\iffalse
 \subsection{Feature Ablation Study}
@@
 Hence, we use every feature to train our model in the next experiments.
+\fi
+%================================================================
 \subsection{Model Scenario}

### 2017-05-23 samplebody-conf.tex
Nambahin bgian feature dan benerin skenario

@@
 
-\subsection{Problem Definitions}
 In this work, we view our problem as a sequence labeling task.
@@
 \subsection{FEATURES}
-Because the small dataset that we have, our model would have a small learning material and an end-to-end approach might not work well.
-As a result, We leveraged nine handcrafted features that help the model in learning.
-\begin{enumerate}
-    \item \textit{Word Embedding.} In the experiments, we use word embedding as input to the neural network.
+Because we have a small dataset, our model would have a small learning material and an end-to-end learning approach will not work well.
+As a result, we leveraged nine handcrafted features that can help our model to characterize sequence of keyphrases.
+Formally, our feature functions is, $f_1, f_2, ..., f_9$, which map a word to a particular feature value.
+
+    \textbf{Word Embedding.} In the experiments, we use word embedding as input to the neural network.
 A skip-gram model \cite{mikolov2013wordembed} was used to generate these 128-dimensional vectors for documents in evaluation data.
@@
 The word embeddings we used in this work were trained using a document that we gathered from Indonesia online forum, medical article, and medical question answering forum.
+Thus, the feature value for the word \texttt{headache} is $f_1(headache) = [v_1, v_2, ..., v_n]$ where $v_i$ is a real value and $n$ is 128.
 
-    \item \textit{Medical Dictionary.} In our experiment, we leveraged a medical knowledge base feature using a medical dictionary.
+    \textbf{Medical Dictionary.} In our experiment, we leveraged a medical knowledge base feature using a medical dictionary.
 Our medical dictionary contains a list of symptom, disease, treatment, and drug in the Indonesian language.
@@
 The original dictionaries contained disease, symptom, treatment, and drug separately in each dictionary.
+For example, $f_2(headache) = [0, 1]$ because \texttt{headache} is disease and inside the dictionary.
 
-    \item \textit{Word Length.} This feature represents the length of each word (i.e., the number of characters in every word).
+    \textbf{Word Length.} This feature represents the length of each word (i.e., the number of characters in every word).
 This feature is based on \cite{cao2010automatically} research on keyphrase extraction in medical question who added word length as a feature because domain-specific words (e.g.
@@
 Thus we use the same feature for Indonesian language.
+For example, $f_3(headache) = [8]$
 
-    \item \textit{Word Postion.} We also adapted word position as feature based on \cite{cao2010automatically}research.
+    \textbf{Word Postion.} We also adapted word position as feature based on \cite{cao2010automatically}research.
 Based on their observation, an important term sometimes appears toward the end of a clinical question.
 For example, "medicine for bell's palsy" appear towards the end of question "what is the best medicine for bell's palsy?".
+Thus, the value of the word \texttt{what} is $f_4(what) = [1]$ because it is on the first position of the sentence.
 
-    \item \textit{POS-tag.} POS-tag of words was also added as our feature.
+    \textbf{POS-tag.} POS-tag of words was also added as our feature.
 POS-tag may give model grammatical information and a better understanding of ambiguous words.
 By our observation, many keyphrases have a common POS pattern.
-For example, "treatment\_Noun for\_Preposition cancer\_Noun", "therapy\_Noun for\_Preposition headache\_Noun".
-Moreover, \cite{skripsiWahid}, and \cite{abacha2011medical} have proven that POS tag feature has a positive contribution in sequence labeling task in Indonesian medical domain such as Medical Entities Recognizer (MER).
+We use Stanford Part-Of-Speech Tagger which pre-trained by Dinakaramani\cite{dinakaramani2014designing}.
+We represent our POS tag feature as one-hot-vector.
+For example, the word \texttt{cancer} has noun tag, $f_5(cancer) = [0, ..,1, ...0]$.
 
-    \item \textit{Medical Entity.} We use medical entity which annotated by \cite{skripsiWahid}.
+    \textbf{Medical Entity.} We use medical entity which annotated by \cite{skripsiWahid} using four categories: drug, treatment, symptom, disease.
 By our observation, medical entities are sometimes part of keyphrases.
 Furthermore, medical entities can provide more information about drug or disease which not available in training data or a medical dictionary.
+We also use one-hot-vector to represent this feature.
+For example, $f_6(cancer) = [0, 0, 0 ,1]$
 
-    \item \textit{Abbreviation and Acronym.} We also identified words by their appearance in abbreviation or acronym dictionary gathered by \cite{skripsiKakAbid}.
+    \textbf{Abbreviation and Acronym.} We also identified words by their appearance in abbreviation or acronym dictionary gathered by \cite{skripsiKakAbid}.
 We observed that important word may not be shortened by the users, such as "cancer", "flu", "bell’s palsy".
+One-hot-vector is used to classify whether a word is an abbreviation/acronym or not.
+For example, the word \texttt{mengapa (why)} sometimes is abbreviated into \texttt{mngp} by some patients.
+Thus, $f_7(mngp) = [0, 1]$
 
-    \item Word Importance.
-We also leveraged a word importance feature.
+    \textbf{Word Importance.} We also leveraged a word importance feature.
 The purpose of this feature is to rank words in a document by their importance.
@@
         \end{equation}
-    \item Word Stickiness.
-As a keyphrase, a sequence must be in a valid order.
+    For example, $f_6(cancer) = [0.56]$.
+    \textbf{Word Stickiness.} As a keyphrase, a sequence must be in a valid order.
 There is some noise such as misuse punctuation by users.
@@
     \end{equation}
-\end{enumerate}
-\subsection{MODEL ARCHITECTURE}
+    For example, the word \texttt{cancer} in sentence "How to prevent cancer doc ?", the feature value is $f_6(cancer) = [0.56, 0.1]$.
+It is worth ti note that the word \texttt{cancer} is rarely co-occur with the word \texttt{doc}.
+
 We process the sequences word by word.
@@
 Finally, we manually annotated those questions.
-The statistical information of our data can be seen in Table \ref{tab:descriptive_stats}
+The statistical information of our data can be seen in Table \ref{tab:descriptive_stats}.
 
@@
 %================================================================
-\subsection{Model Scenario}
+\subsection{Results}
 We created a scenario to evaluate the performance of our model.
-In this scenario, we also compared our model to an unsupervised learning algorithm using RAKE.
-Moreover, we also implemented CRF to as a baseline for this sequence labeling task.
-CRF also has been proven effective in extracting keyphrases \cite{cao2010automatically} \cite{zhang2008automatic}.
-The following scenarios are listed below:
-\begin{itemize}
-	\item RAKE
-	\item CRF
-	\item B-LSTM
-	\item CNN-B-LSTM
-	\item Weighting-CNN-B-LSTM
-\end{itemize}
+In this scenario, we also compared our model to an unsupervised learning algorithm using RAKE \cite{rake} and a supervised learning algorithm CRF task.
+We also conducted an experiment to compare the effectiveness of our CNN layer.
+Furthermore, we also compared our model with (CNN-B-LSTM) or without weighting layer (W-CNN-B-LSTM).
 The result of the scenario can be seen in Table \ref{tab:model_scenario}.
@@
 
+		W-CNN-B-LSTM & 81.08\% & 81.18\% & 81.01\% \\
 		\bottomrule
@@
 The experiment results indicated our context aware CNN and B-LSTM worked well in keyphrase extraction in Indonesian user-generated medical domain.
+We also tried our feature weighting layer in our best model which is CNN with B-LSTM and fully-connected hidden layer on top.
+The result shows that our weighting layer not worked quite well.
 
-We also tried our feature weighting layer in our best model which is CNN with B-LSTM and fully-connected hidden layer on top.
-The result in Table \ref{tab:weighting_scenario} shows that our weighting layer not worked quite well.
-We suspect the gap of information between features are on of the reason which cause the result drop
-\begin{table}
-	\caption{Weighting Layer Scenario Result}
-	\label{tab:weighting_scenario}
-	\begin{tabular}{lccc}
-		\toprule
-		Models&Precision&Recall&F-Measure\\
-		\midrule
-		CNN-B-LSTM & 82.00\% & 82.99\% & 82.41\% \\
-
-		W-CNN-B-LSTM & 81.08\% & 81.18\% & 81.01\% \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-\subsection{Error Analysis}
+\subsection{Other Analysis}
 We performed an error analysis to the aforementioned model, the result shown there are several errors.

### 2017-05-23 sample-sigconf.tex
Add several formula
Add formula, contoh, dan tabel
Cut introduction
Nambahin bgian feature dan benerin skenario
Change Conclusion

@@
 
-\title{SIG Proceedings Paper in LaTeX Format}
+\title{Keyphrase Extraction from User Generated Content on Medical Domain}
+\iffalse
 \titlenote{Produces the permission block, and
@@
   \texttt{acmart.pdf} document}
+\fi
 
 % The default list of authors is too long for headers}
-\renewcommand{\shortauthors}{B. Trovato et al.}
+\renewcommand{\shortauthors}{F. Ilham et al.}
 
@@
 Reducing the complex characteristics of contents, including but not limited to linguistic variations, into structured information can help the text interpretation process.
-A common approach is to extract medical terms from each document using available tools, such as medical entity recognizer.
-However, we argue that there are many missing pieces of information when we rely only on medical entities or keywords as main information.
+We argue that there are many missing pieces of information when we rely only on medical entities or keywords as main information.
 Hence, we use keyphrases extraction techniques to extract more important information about the concept of the document.
@@
 
-\keywords{ACM proceedings, \LaTeX, text tagging}
+\keywords{keyphrase extraction, health-related text mining, deep learning, recurrent neural networks, convolutional neural networks}
 
@@
 \end{document}
+\grid

### 2017-05-23 samplebody-conf.tex
Change Conclusion

@@
 
-	Dok , saya sering sekali merasa \textbf{kram pada perut kanan bagian atas} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}.
+	\texttt{Dok , saya sering sekali merasa \textbf{kram pada perut kanan bagian atas} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}.
 Dan saat kambuh seperti itu, \textbf{nafas sangat sakit}.
@@
 How is the treatment when it's occur?
-thanks before \\
+thanks before)}
 
@@
 That is, given a medical question containing $N$ words $w = (w_1, w_2,...,w_N$, we want to find the best sequence pf labels $y = (y_1, y_2,..., y_N)$, in which each label is determined using probabilities \\$P(y_i|w_{i-l},...,w_{i+l},y_{i-l},...,y_{i+l})$ \\where $l$ is a small number.
-\subsection{FEATURES}
+
 Because we have a small dataset, our model would have a small learning material and an end-to-end learning approach will not work well.
@@
 But our model, failed to capture that connection, it extracted "treatment for headache" and "sore throat" separately.
+
 \section{Conclusion}
+We have proposed a model to address the task of keyphrase extraction on Indonesian user-generated medical domain.
+Extracting information patient intentions and needs on user-generated medical content is not a trivial task due to the fact that the content are usually short, contain many medical terms, and written in an unstructured format, as opposed to formal text.
+Our model is based on sequence labeling task that employs deep learning approach using convolutional neural networks and bi-directional lstm.
+Several handcrafted features were proposed, including word importance to detect important word in a document and word stickiness for handling unstructured writing.
+Although our model outperforms baseline models, further improvements are needed especially in evaluation method which cannot cover the whole problem.
+\iffalse
 We investigate a keyphrase extraction problem especially in Indonesian medical questions domain with sequence labeling approach.
@@
 Thus partial evaluation failed to capture that problem.
+\fi

### 2017-05-23 samplebody-conf.tex
Edit results

@@
 Finally, every candidate keyphrase in the document will be classified as either a keyphrase or non-keyphrase.
-The well known method for this approach is KEA \cite{witten1999kea}, they use machine-learning (i.e., Naive Bayes)for classifying candidate keyphrases.
+The well known method for this approach is KEA \cite{witten1999kea}, they use machine-learning (i.e., Naive Bayes) for classifying candidate keyphrases.
 The utilization of neural networks in classifying candidate keyphrases also conducted by \cite{ekpNeuralNetworks}.
@@
 They use stopwords to split candidate keyphrases, then candidates are ranked with two aspects: PF-IDF (Phrase Frequency * Inverse Document Frequency) and domain knowledge which is extracted from medical article.
-In terms of medical social media content, \cite{cao2010automatically} use Conditional Random Fields (CRFs) for extracting keywords from medical questions in online health-forum.
+In terms of user-generated medical content, \cite{cao2010automatically} use Conditional Random Fields (CRFs) for extracting keywords from medical questions in online health-forum.
 They use information, such as word location and length as features in their experiments.
@@
 By our observation, many keyphrases have a common POS pattern.
-We use Stanford Part-Of-Speech Tagger which pre-trained by Dinakaramani\cite{dinakaramani2014designing}.
+We use Stanford Part-Of-Speech Tagger which pre-trained by Dinakaramani \cite{dinakaramani2014designing}.
 We represent our POS tag feature as one-hot-vector.
@@
 
-    \textbf{Word Importance.} We also leveraged a word importance feature.
-The purpose of this feature is to rank words in a document by their importance.
-The "keywordness" value of a word can be determined by the importance value.
+    \textbf{Word Importance.} The purpose of this feature is to rank words in a document by their importance.
 To extract this feature, we adapted a method from TextRank \cite{mihalcea2004textrank} algorithm for ranking words in a document.
 They represent words as vertices in graph and the distance between words as edges.
-However, in building an indirect graph, we use a word similarity by using our trained word embedding model.
+However, in building an indirected graph, we use a word similarity by using our pre-trained word embedding model as weight for edges.
 Two words have a connected edge, if their similarity is not negative.
-The weight of the edge is the similarity itself.
 Moreover, we use a modified PageRank \cite{page1999pagerank} algorithm that consider edges weight in the calculation.
@@
 We process the sequences word by word.
-Features are extracted from every word as the input representation of the model.
-The output for this words are label which describe a word is either part of keyphrase or not.
+All Features are extracted and concatenated into one vector from every word as the input representation of the model.
+The output of our model are label which describe whether a word is either part of keyphrase or not.
 
-To give our model a better insight of context, we introduce Convolutional Neural Networks (CNNs) to capture context from three adjacent words.
-From our observation, to know whether a word is part of keyphrase or not, we need to know the context of the word itself.
+We introduce Convolutional Neural Networks (CNNs) to exploit high level features between neighboring word positions.
+Based on our observation, a keyphrase is.
 For example, "Doc, i have a frequent back pain.
@@
 With CNNs, we argue that our model can capture the surrounding information of a word.
+The output of the CNNs layer will be fed into our next layer which is B-LSTM.
 
-To get a better inference, information from the past and future sequences can be integrated.
+To get a better inference, information from the past and future of sequences can be integrated.
 This approach is proven effective  in sequence labeling task such as semantic role labeling \cite{SMRzhou2015end} and named entity recognition \cite{ma2016end}.
-Hence, we utilized  bi-directional LSTM (B-LSTM) for extracting structural knowledge by processing sequences both forward and backward.
+Therefore, we utilized  bi-directional LSTM (B-LSTM) for extracting structural knowledge by processing sequences both forward and backward.
 We build up to two layers of B-LSTM.
-To perform the sequence tagging task, we build a fully connected layer in the top of our model. This layer will classify the output of our model with softmax activation function.
+
+In order to perform the sequence tagging task, we build a fully connected layer in the top of our model. This layer will classify the output of our model with softmax activation function.
 
 We also experimented on customizing the way we input the features underneath our aforementioned networks.
-Instead of concatenating all feature into one vector, we tried to give weight for every feature we have.
+Instead of concatenating all features into one vector, we tried to give weight for every feature we have.
 We argue that each feature have different contribution to the model.
 In order to do so, we create a new layer underneath our model to do the weighting scenario.
-The following equation to weight all feature can be seen in below:
+The following equation to weight all features can be seen in below:
 \begin{equation}
@@
 \subsection{Results}
-We created a scenario to evaluate the performance of our model.
-In this scenario, we also compared our model to an unsupervised learning algorithm using RAKE \cite{rake} and a supervised learning algorithm CRF task.
-We also conducted an experiment to compare the effectiveness of our CNN layer.
-Furthermore, we also compared our model with (CNN-B-LSTM) or without weighting layer (W-CNN-B-LSTM).
-The result of the scenario can be seen in Table \ref{tab:model_scenario}.
 \begin{table}
@@
 
-		LSTM & 78.77\% & 79.71\% & 79.16\% \\
-
 		B-LSTM & 81.88\% & \textbf{83.05\%} & 82.37\% \\
@@
 \end{table}
-Table \ref{tab:model_scenario} shows the performance of different methods that we proposed on the dataset we have.
-To evaluate or model we use 10-cross fold validation.
-From the results, we observed that every supervised method using sequence labeling approach achieved a better performance than RAKE.
-The best result achieved by CNN with two stacked B-LSTM with 82.41\% F-Score.
-RAKE Perform the worst.
-The result shows that RAKE only achieved 52.9\% F-Score.
-This is because RAKE using statistical approach to weight candidate keyphrases which become a problem in short document like medical questions.
-Furthermore, RAKE using stopwords to split candidate keyphrases in document, but user-generated content tend to have a bad structural information.
-Thus there are some misplaced stopwords in the content.
-Among other methods, CRF performed the worst.
-Bidirectional approach shows effectiveness because B-LSTM has a better result than LSTM.
-Furthermore, using CNN to capture context between words also shows improvement and it become the best result in our experiment.
-However, when we use CRF on the top of our model the results dropped.
-The experiment results indicated our context aware CNN and B-LSTM worked well in keyphrase extraction in Indonesian user-generated medical domain.
-We also tried our feature weighting layer in our best model which is CNN with B-LSTM and fully-connected hidden layer on top.
-The result shows that our weighting layer not worked quite well.
+We created a scenario to evaluate the performance of our model.
+In this scenario, we also compared our model to an unsupervised learning algorithm using RAKE \cite{rake} and a supervised learning algorithm CRF task.
+We also conducted an experiment to proof the effectiveness of our CNN layer by comparing plain B-LSTM and B-LSTM with .s layer(CNN-B-LSTM).
+Furthermore, we also compared our model with or without weighting layer (W-CNN-B-LSTM).
+
+For comparison, we implemented RAKE \cite{rake} and CRF \cite{zhang2008automatic}, which use unsupervised and supervised approach. For CRF, we use the same features proposed above.
+
+As we can see in Table \ref{tab:model_scenario}, RAKE and CRF underperformed on Indonesian user-generated medical question since RAKE were specially devised for formal text.
+By our observation of the result provided by CRF, the method failed to predict long sequences as keyphrase.
+
+Our CNNs layer also shows improvement in precision and F1 score.
+From the result above, we suggest that CNNs layer can extract more features implicitly from neighboring words.
+However, our weighting layer failed to provide some improvement.
+We argue that weighting layer have a significant information loss when converting features vector.
 
 \subsection{Other Analysis}
-We performed an error analysis to the aforementioned model, the result shown there are several errors.
+We performed an analysis to the aforementioned model, the result shown there are several errors.
 Some of the error are uncompleted keyphrases.
@@
 Several handcrafted features were proposed, including word importance to detect important word in a document and word stickiness for handling unstructured writing.
-Although our model outperforms baseline models, further improvements are needed especially in evaluation method which cannot cover the whole problem.
+Although our model outperforms state of the art methods for keyphrase extraction, further improvements are needed especially in evaluation method which cannot cover the whole problem.
 \iffalse
 We investigate a keyphrase extraction problem especially in Indonesian medical questions domain with sequence labeling approach.
-We leverage a deep learning approach using CNN and B-LSTM.
+We leverage a deep learning approach using CNNsand B-LSTM.
 Moreover, we also extracted nine features that capture medical concepts from a knowledge base, and linguistic components as our features.

### 2017-05-23 samplebody-conf.tex
edit foot note and several things

@@
 
-In this paper, we only focus the task of keyphrase extraction on Indonesian medical questions in online forum ,such as alodokter, health detik, doktergratis, dokter.id, doktersehat, klikdokter \footnote{www.alodokter.com, health.detik.com, www.dokter.id, www.doktersehat.com, www.klikdokter.com}.
+In this paper, we only focus the task of keyphrase extraction on Indonesian medical questions in online forum ,such as alodokter\footnote{www.alodokter.com}, health detik \footnote{health.detik.com}, dokter.id \footnote{www.dokter.id}, klikdokter \footnote{www.klikdokter.com}.
 We present new keyphrases extraction techniques to extract more important information about the patient intentions and needs, which expressed inside Indonesian medical questions.

### 2017-05-24 paper-content.tex
Revise From Pak Alfan

--- 2017-05-23 samplebody-conf.tex
@@
 \section{Introduction}
-
-There are tremendous amount of user-generated contents about medical information through the internet.
+There are a tremendous amount of user-generated contents about medical information through the internet.
 As a result, there is a growing need for enriching medical-related knowledge, for which it can be very valuable for several tasks, such as medical document retrieval, medical question answering, and health-related text mining applications \cite{cao2010automatically}.
-However, understanding those various health-related contents, especially from online forum, is simply not a trivial task since they are written in free text format (i.e.
+However, understanding those various health-related contents, especially from an online forum, is simply not a trivial task since they are written in free text format (i.e.
 unstructured format), and often prone to grammatical and typographical glitches.
@@
 
-One possible solution is to extract medical terms that represents the document they belong to.
+One possible solution is to extract medical terms that represent the document they belong to.
 The common approach is harnessing medical entity recognizer.
@@
 Keyphrases are usually selected phrases or clauses that can capture the main topic of a given document \cite{turney2000learning}.
-They can provide readers with highly valuable and representative information, such that looking at keyphrases is sufficient to understand the whole body of document.
+They can provide readers with highly valuable and representative information, such that looking at keyphrases is sufficient to understand the whole body of a document.
 
-In this paper, we only focus the task of keyphrase extraction on Indonesian medical questions in online forum ,such as alodokter\footnote{www.alodokter.com}, health detik \footnote{health.detik.com}, dokter.id \footnote{www.dokter.id}, klikdokter \footnote{www.klikdokter.com}.
-We present new keyphrases extraction techniques to extract more important information about the patient intentions and needs, which expressed inside Indonesian medical questions.
-Furthermore, we also propose a new definition of keyphrases, which is based on our observation of health-related and user-generated document.
+In this paper, we only focus the task of keyphrase extraction on Indonesian medical questions from online forums, such as alodokter\footnote{www.alodokter.com}, health detik \footnote{health.detik.com}, dokter.id \footnote{www.dokter.id}, klikdokter \footnote{www.klikdokter.com}.
+We present a new keyphrase extraction techniques to extract more important information about the patient intentions and needs, which expressed inside Indonesian medical questions.
+Furthermore, we also propose a new definition of keyphrases, which is based on our observation of health-related and user-generated questions.
 Actually, our final goal is to develop medical question answering systems to assist physicians or people obtaining health information.
-The work presented in this paper is absolutely inline with our goal, since important keyphrases of a question document can be used to formulate a query for the passage retrieval subsystem \cite{gong2009improving}.
-The example of keyphrase extraction in medical document can be seen below:
-
-	\texttt{Dok , saya sering sekali merasa \textbf{kram pada perut kanan bagian atas} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}.
+The work presented in this paper is absolutely in line with our goal since important keyphrases of a medical question can be used to formulate a query for the passage or question retrieval subsystem \cite{gong2009improving}.
+The following example shows the results of keyphrase extraction in a medical document:
+	\textit{\\Dok , saya sering sekali merasa \textbf{\emph{kram pada perut kanan bagian atas}} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}.
 Dan saat kambuh seperti itu, \textbf{nafas sangat sakit}.
 Seminggu yang lalu sampai terkapar karena tidak kuat menahan sakitnya saat bernafas.
-bagaimana penanggulangannya saat kambuh?
-terima kasih sblumnya dok.
-\\\\
-	(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}.
+apakah ada hubungannya dengan \textbf{diet mayo}?
+terima kasih sblumnya dok.}
+	\texttt{(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}.
 And when the symptom occur it's \textbf{very hurt when breathing}.
 Last week i fainted because cannot hold the pain when i was breathing.
-How is the treatment when it's occur?
+is there any connection with \textbf{moyo diet}?
 thanks before)}
+It can be seen on the example that keyphrases can be a word, phrase, or even clause.
+Furthermore, there are many grammatical errors and abbreviation, such as \texttt{sy} for the replacement of the word \texttt{saya (I)}.
+It is also worth to note that keyphrase \texttt{diet mayo (mayo diet)} is not part of medical entity listed by Wahid \cite{skripsiWahid} and Abid \cite{skripsiKakAbid} research.
+Thus, extracting keyphrase for getting patient needs is not a trivial task.
 
-It can be seen on the example that keyphrases can be a word, phrase, or even clause.
-Furthermore, there are many grammatical error in user-generated document that make the extraction process not trivial.
-
-In our work, we use the same approach as \cite{cao2010automatically}, which treats keyphrase extraction as a sequence labeling task.
-In our experiment, we employed and combined various deep learning architectures, such as convolutional neural networks and bi-directional long short-term memory networks, to exploit high level features between neighboring word positions.
+In our work, we use similar approach as in Cao et al.
+\cite{cao2010automatically}, which treats keyphrase extraction as a sequence labeling task.
+The difference is that, in our experiment, we employed and combined various deep learning architectures, such as convolutional neural networks and bi-directional long short-term memory networks, to exploit high level features between neighboring word positions.
 To improve the quality of our model, we leverage several new hand-crafted features that can handle our keyphrase extraction problems in medical user-generated content, such as word importance and word stickiness features.
@@
 The more important a word is to the content of document, the higher its "keywordness" value would seem to be.
-In addition, we also propose word stickiness feature to make our model constructs keyphrases better.
+In addition, we also propose word stickiness feature to make our model constructs keyphrases
 %===========Unused Introduction========================
@@
 For example, we give a medical question asked by a patient in Indonesian language:
-\begin{itemize}
-    \item 
-		Dok , saya sering sekali merasa \textbf{kram pada perut kanan bagian atas} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}.
+	\textit{\\Dok , saya sering sekali merasa \textbf{\emph{kram pada perut kanan bagian atas}} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}.
 Dan saat kambuh seperti itu, \textbf{nafas sangat sakit}.
 Seminggu yang lalu sampai terkapar karena tidak kuat menahan sakitnya saat bernafas.
-bagaimana penanggulangannya saat kambuh?
-terima kasih sblumnya dok.
-\\\\
-		(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}.
+apakah ada hubungannya dengan \textbf{diet mayo}?
+terima kasih sblumnya dok.}
+	\texttt{(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}.
 And when the symptom occur it's \textbf{very hurt when breathing}.
 Last week i fainted because cannot hold the pain when i was breathing.
-How is the treatment when it's occur?
-thanks before) \\
-\end{itemize}
-It can be seen that keyphrases can be a word, phrase, or even clause. Furthermore, there are many grammatical error in the document that make the extraction process not trivial.
+is there any connection with \textbf{moyo diet}?
+thanks before)}
+
+It can be seen on the example that keyphrases can be a word,
+phrase, or even clause. Furthermore, there are many grammatical
+errors and abbreviation, such as sy for the replacement of the word
+saya (I). It is also worth to note that keyphrase diet mayo (mayo
+diet) is not part of medical entity listed by Wahid [9] and Abid
+[4] research. Thus, extracting keyphrase for getting patient needs
+is not a trivial task.
 
@@
 For the unsupervised line of research, keyphrase extraction is formulated as a ranking problem, in which each candidate keyphrase is assigned a score that represents its keywordness value.
-The well known researches in unsupervised approach are \cite{rake} which use the ratio of word degree and frequency to rank terms.
-\cite{mihalcea2004textrank} developed a graph based approach which treats words as vertices and construct edges between words using co-occurrence.
+The well-known research in unsupervised approach are RAKE \cite{rake} which use the ratio of word degree and frequency to rank terms.
+Mihalcea and Tarau \cite{mihalcea2004textrank} developed a graph-based approach which treats words as vertices and constructs edge between words using co-occurrence.
 
@@
 Finally, every candidate keyphrase in the document will be classified as either a keyphrase or non-keyphrase.
-The well known method for this approach is KEA \cite{witten1999kea}, they use machine-learning (i.e., Naive Bayes) for classifying candidate keyphrases.
+The well-known method for this approach is KEA \cite{witten1999kea}, they use machine-learning (i.e., Naive Bayes) for classifying candidate keyphrases.
 The utilization of neural networks in classifying candidate keyphrases also conducted by \cite{ekpNeuralNetworks}.
@@
 
-Unfortunately, there are limited works regarding the task of keyphrase extraction in medical domain.
+Unfortunately, there are limited works regarding the task of keyphrase extraction in medical domain, especially in Indonesian language.
 \cite{ekpMedicalDocumentHybrid} use a hybrid medical knowledge base and statistical approach to extract keyphrases from medical articles.
 They use stopwords to split candidate keyphrases, then candidates are ranked with two aspects: PF-IDF (Phrase Frequency * Inverse Document Frequency) and domain knowledge which is extracted from medical article.
-In terms of user-generated medical content, \cite{cao2010automatically} use Conditional Random Fields (CRFs) for extracting keywords from medical questions in online health-forum.
+In terms of user-generated medical content, \cite{cao2010automatically} use Conditional Random Fields (CRFs) for extracting keywords from medical questions in online health forum.
 They use information, such as word location and length as features in their experiments.
@@
 MAUI itself is an improvement to the aforementioned supervised model, KEA.
-Furthermore, \cite{marujoMAUI} use word embedding and brown clustering as features.
+Furthermore, Marujo et al., \cite{marujoMAUI} use word embedding and brown clustering as features.
 Their experiment result had shown that the proposed features and MAUI performs better than statistical methods, such as simple tf-idf approach.
@@
 The utilization of neural networks is also quite popular in the recent years.
-\cite{ekpNeuralNetworks} uses Feed Forward Neural Networks to classify candidate keyphrases.
+Sarkar and Kamal \cite{ekpNeuralNetworks} use Feed Forward Neural Networks to classify candidate keyphrases.
 To extract candidate keyphrases, they use POS tag information for classifying all words in the document.
 Then, Deterministic Finite Automation (DFA) is used to extract noun phrases as candidate keyphrases.
-Furthermore, deep neural networks is also employed for extracting keyphrase, like the one proposed by \cite{zhang2016keyphrase}, that uses joint Recurrent Neural Networks (RNNs) layer to capture keyphrase sequences in microblogs.
+Furthermore, deep neural networks is also employed for extracting keyphrase, like the one proposed by Zhang et al., \cite{zhang2016keyphrase}, that uses joint Recurrent Neural Networks (RNNs) layer to capture keyphrase sequences in microblogs.
 The research had shown that RNN is very effective to extract keyword.
@@
 To analyze the effectiveness of our model for keyphrase extraction in user-generated medical domain, we constructed an evaluation dataset.
-A a number of questions was gathered from Indonesian medical question answering forum.
+A number of questions was gathered from Indonesian medical question answering forum.
 The data was crawled by \cite{skripsiKakRadit} and \cite{skripsiWahid} in their experiment.
@@
 In Table X, we give an example sequence with labels for each word.
-The statistical information of the dataset can be seen in Table \ref{tab:descriptive_stats}.
-\begin{table}
-	\caption{Statistical information of dataset.
-W, K, $\bar{N}_{w}$, $\bar{N}_{k}$ are the total of words, number of keyphrases, average number of words, and average number of keyphrases in each question, respectively.}
-	\label{tab:descriptive_stats}
-	\begin{tabular}{lcccc}
-		\toprule
-		\#questions&W&K&$\bar{N}_{w}$&$\bar{N}_{k}$\\
-		\midrule
-		416 & 26747  & 64.76 & 1861 & 4.49 \\
-
-		\bottomrule
-	\end{tabular}
-\end{table}
+The statistical information of the dataset can be seen in Table
 \fi
 
-In this work, we view our problem as a sequence labeling task.
-That is, given a medical question containing $N$ words $w = (w_1, w_2,...,w_N$, we want to find the best sequence pf labels $y = (y_1, y_2,..., y_N)$, in which each label is determined using probabilities \\$P(y_i|w_{i-l},...,w_{i+l},y_{i-l},...,y_{i+l})$ \\where $l$ is a small number.
+In this work, we view keyphrase extraction problem as a sequence labeling task.
+That is, given a medical question containing $N$ words $w = (w_1, w_2,...,w_N)$, we want to find the best sequence pf labels $y = (y_1, y_2,..., y_N)$, in which each label is determined using probabilities $P(y_i|w_{i-l},...,w_{i+l},y_{i-l},...,y_{i+l})$ where $l$ is a small number.
 
 Because we have a small dataset, our model would have a small learning material and an end-to-end learning approach will not work well.
-As a result, we leveraged nine handcrafted features that can help our model to characterize sequence of keyphrases.
-Formally, our feature functions is, $f_1, f_2, ..., f_9$, which map a word to a particular feature value.
+As a result, we leveraged nine handcrafted features that can help our model to characterize the sequence of keyphrases.
+Formally, our feature functions are, $f_1, f_2, ..., f_9$, which map a word to a particular feature value.
 
@@
 A skip-gram model \cite{mikolov2013wordembed} was used to generate these 128-dimensional vectors for documents in evaluation data.
-The dimension of the vector were chosen based on \cite{skripsiWahid} experiment.
+The dimension of the vector was chosen based on \cite{skripsiWahid} experiment.
 The word embeddings we used in this work were trained using a document that we gathered from Indonesia online forum, medical article, and medical question answering forum.
@@
 
-    \textbf{Word Postion.} We also adapted word position as feature based on \cite{cao2010automatically}research.
+\textbf{Word Position.} We also adapted word position as feature based on \cite{cao2010automatically}research.
 Based on their observation, an important term sometimes appears toward the end of a clinical question.
-For example, "medicine for bell's palsy" appear towards the end of question "what is the best medicine for bell's palsy?".
-Thus, the value of the word \texttt{what} is $f_4(what) = [1]$ because it is on the first position of the sentence.
+For example, "medicine for bell's palsy" appear towards the end of a question "what is the best medicine for bell's palsy?".
+Thus, the value of the word \texttt{palsy} is $f_4(palsy) = [8]$ because it is on the first position of the sentence.
 
@@
 To extract this feature, we adapted a method from TextRank \cite{mihalcea2004textrank} algorithm for ranking words in a document.
-They represent words as vertices in graph and the distance between words as edges.
-However, in building an indirected graph, we use a word similarity by using our pre-trained word embedding model as weight for edges.
-Two words have a connected edge, if their similarity is not negative.
+They represent words as vertices in the graph and the distance between words as edges.
+However, in building an undirected graph, we use a word similarity by using our pre-trained word embedding model as a weight for edges.
+Two words have a connected edge if their similarity is not negative.
 Moreover, we use a modified PageRank \cite{page1999pagerank} algorithm that consider edges weight in the calculation.
 Formally, let $G = (V, E)$ be an undirected graph with the set of vertices V and set of edges E, where E is a subset of $VxV$.
-For a given vertex $V_i$ let $In(V_i)$ be the set of vertices that point to it (predecessors), and let $Out(V_i)$ be the set of vertices that vertex $V_i$ points to (successors).
+For a given vertex $V_i$ let $In(V_i)$ be the set of vertices that point to it (predecessors) and let $Out(V_i)$ be the set of vertices that vertex $V_i$ points to (successors).
 The modified PageRank formula that proposed by \cite{mihalcea2004textrank} can be seen in Formula \ref{eq:pagerank}.
@@
 We use Pointwise Mutual Information (PMI) of a bigram probability to capture the likeness.
-This feature represented as two dimensional vector $v = [x1, x2]$, with $x_1$ is the PMI with the word before and $x_2$ is the PMI with the word after.
+This feature represented as two-dimensional vector $v = [x1, x2]$, with $x_1$ is the PMI with the word before and $x_2$ is the PMI with the word after.
 Formula \ref{eq:pmi} is the formula for calculating the PMI value.
@@
 All Features are extracted and concatenated into one vector from every word as the input representation of the model.
-The output of our model are label which describe whether a word is either part of keyphrase or not.
+The output of our model are labels which describe whether a word is either part of keyphrase or not.
 
-We introduce Convolutional Neural Networks (CNNs) to exploit high level features between neighboring word positions.
+We introduce Convolutional Neural Networks (CNNs) to exploit high-level features between neighboring word positions.
 Based on our observation, a keyphrase is.
-For example, "Doc, i have a frequent back pain.
+For example, "Doc, I have a frequent back pain.
 What happen?".
-The keyphrase for previous example is "frequent back pain".
-In order to know that "back" is part of keyphrase, we need information from the word "frequent" which give an intensity of a symptom and "pain" which refer to "back pain" as main term.
+The keyphrase for the previous example is "frequent back pain".
+In order to know that "back" is part of keyphrase, we need information from the word "frequent" which give an intensity of a symptom and "pain" which refer to "back pain" as the main term.
 With CNNs, we argue that our model can capture the surrounding information of a word.
@@
 Instead of concatenating all features into one vector, we tried to give weight for every feature we have.
-We argue that each feature have different contribution to the model.
+We argue that each feature has different contribution to the model.
 In order to do so, we create a new layer underneath our model to do the weighting scenario.
@@
 This evaluation is used because we treat keyphrases as sequences of words.
-Thus we can use partial evaluation which is used to evaluate Named Entity Recognition system.
-In partial evaluation method, a assigned keyphrase is predicted correctly if a predicted keyphrase has a word which is a subset in assigned keyphrase words.
+Thus we can use partial evaluation which is used to evaluate Named Entity Recognition system \cite{seki2003probabilistic}.
 
@@
 In this scenario, we also compared our model to an unsupervised learning algorithm using RAKE \cite{rake} and a supervised learning algorithm CRF task.
-We also conducted an experiment to proof the effectiveness of our CNN layer by comparing plain B-LSTM and B-LSTM with .s layer(CNN-B-LSTM).
+We also conducted an experiment to proof the effectiveness of our CNN layer by comparing standard B-LSTM and B-LSTM with CNNs layer(CNN-B-LSTM).
 Furthermore, we also compared our model with or without weighting layer (W-CNN-B-LSTM).
@@
 As we can see in Table \ref{tab:model_scenario}, RAKE and CRF underperformed on Indonesian user-generated medical question since RAKE were specially devised for formal text.
-By our observation of the result provided by CRF, the method failed to predict long sequences as keyphrase.
+By our observation of the result provided by CRF, the method failed to predict long sequences as a keyphrase.
 
@@
 However, our weighting layer failed to provide some improvement.
-We argue that weighting layer have a significant information loss when converting features vector.
+We argue that weighting layer has a significant information loss when converting features vector.
 
@@
 Moreover, there are also special case for keyphrases like "treatment for headache and sore throat (penyembuhan untuk sakit kepala dan tenggorokan)", that keyphrase need to be captured as whole because "sore throat" have a connection with the word "treatment".
-But our model, failed to capture that connection, it extracted "treatment for headache" and "sore throat" separately.
+But our model failed to capture that connection, it extracted "treatment for headache" and "sore throat" separately.
 
@@
 We have proposed a model to address the task of keyphrase extraction on Indonesian user-generated medical domain.
-Extracting information patient intentions and needs on user-generated medical content is not a trivial task due to the fact that the content are usually short, contain many medical terms, and written in an unstructured format, as opposed to formal text.
+Extracting information patient intentions and needs on user-generated medical content is not a trivial task due to the fact that the content is usually short, contain many medical terms, and written in an unstructured format, as opposed to formal text.
 Our model is based on sequence labeling task that employs deep learning approach using convolutional neural networks and bi-directional lstm.

### 2017-05-24 paper.tex
Revise From Pak Alfan

--- 2017-05-23 sample-sigconf.tex
@@
 % DOI
+\iffalse
 \acmDOI{10.475/123_4}
@@
 \acmPrice{15.00}
+\fi
 
@@
 
-\title{Keyphrase Extraction from User Generated Content on Medical Domain}
+\title{Keyphrase Extraction from User Generated Contents on Medical Domain}
 \iffalse
@@
 % The default list of authors is too long for headers}
-\renewcommand{\shortauthors}{F. Ilham et al.}
+%\renewcommand{\shortauthors}{F. Ilham et al.}
 
@@
 Understanding those various contents is simply not a trivial task.
-Reducing the complex characteristics of contents, including but not limited to linguistic variations, into structured information can help the text interpretation process.
-We argue that there are many missing pieces of information when we rely only on medical entities or keywords as main information.
-Hence, we use keyphrases extraction techniques to extract more important information about the concept of the document.
-Previous works in keyphrases extraction mostly focused on a general domain, long and formal written documents.
-These methods perform poorly when being applied to user-generated contents and medical documents.
-In this work, we propose deep bi-directional recurrent network and convolutional neural network as a model for extracting keyphrases.
-Furthermore, we leveraged word embedding, medical concepts from a knowledge base, and linguistic components as our features.
+Therefore, reducing the complex characteristics of the contents into structured information could be very beneficial for the text interpretation process.
+We argue that there are many missing pieces of information when we rely merely on medical entities (i.e., using Medical Entity Recognizer) as our main information.
+In our work, we use keyphrases extraction techniques to extract more important information about the concept of the document.
+Previous works on keyphrases extraction mostly focused on a general domain, long and formal written documents, which make them perform poorly when being applied to user-generated contents and medical documents.
+Moreover, we propose several deep learning architectures, such as bi-directional long-short term memory networks, convolutional neural networks, and their combinations as the models for extracting keyphrases.
+Furthermore, we leverage word embeddings, medical concepts from a knowledge base, and linguistic components as our features.
 The proposed algorithm achieved F1 score of 82.41\%.
@@
 %
+\iffalse
 \begin{CCSXML}
@@
 \ccsdesc[100]{Networks~Network reliability}
+\fi
 
@@
 
-\input{samplebody-conf}
+\input{paper-content}
 
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sigproc}
+\bibliography{reference}
 

### 2017-05-24 acmart.ins.sh

@@ -1,0 +1,3 @@
+#!/bin/sh
+mogrify -crop 1000x803+0+0 acmart.ins.png
+exit 0

### 2017-05-24 sample-sigconf.tex
Edit results
edit foot note and several things
Updates from ShareLaTeX

@@
 \end{CCSXML}
-
+\iffalse
 \ccsdesc[500]{Computer systems organization~Embedded systems}

### 2017-05-24 samplebody-conf.tex
Updates from ShareLaTeX

@@
 
-In this paper, we only focus the task of keyphrase extraction on Indonesian medical questions in online forum ,such as alodokter\footnote{www.alodokter.com}, health detik \footnote{health.detik.com}, dokter.id \footnote{www.dokter.id}, klikdokter \footnote{www.klikdokter.com}.
+In this paper, we only focus the task of keyphrase extraction on Indonesian medical questions in online forum ,such as \textit{alodokter}\footnote{www.alodokter.com}, \textit{health detik} \footnote{health.detik.com}, \textit{dokter.id} \footnote{www.dokter.id}, \textit{klikdokter} \footnote{www.klikdokter.com}.
 We present new keyphrases extraction techniques to extract more important information about the patient intentions and needs, which expressed inside Indonesian medical questions.
@@
 The work presented in this paper is absolutely inline with our goal, since important keyphrases of a question document can be used to formulate a query for the passage retrieval subsystem \cite{gong2009improving}.
-The example of keyphrase extraction in medical document can be seen below:
+The following example shows the results of keyphrase extraction in a medical document:
 
-	\texttt{Dok , saya sering sekali merasa \textbf{kram pada perut kanan bagian atas} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}.
+	\textit{\\Dok , saya sering sekali merasa \textbf{\emph{kram pada perut kanan bagian atas}} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}.
 Dan saat kambuh seperti itu, \textbf{nafas sangat sakit}.
@@
 bagaimana penanggulangannya saat kambuh?
-terima kasih sblumnya dok.
-\\\\
-	(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}.
+terima kasih sblumnya dok.}
+	\texttt{(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}.
 And when the symptom occur it's \textbf{very hurt when breathing}.
 Last week i fainted because cannot hold the pain when i was breathing.
-How is the treatment when it's occur?
+How's the treatment when it occurs?
 thanks before)}
@@
 
-In our work, we use the same approach as \cite{cao2010automatically}, which treats keyphrase extraction as a sequence labeling task.
-In our experiment, we employed and combined various deep learning architectures, such as convolutional neural networks and bi-directional long short-term memory networks, to exploit high level features between neighboring word positions.
+In our work, we use similar approach as in Cao et al.
+\cite{cao2010automatically}, which treats keyphrase extraction as a sequence labeling task.
+The difference is that, in our experiment, we employed and combined various deep learning architectures, such as convolutional neural networks and bi-directional long short-term memory networks, to exploit high level features between neighboring word positions.
 To improve the quality of our model, we leverage several new hand-crafted features that can handle our keyphrase extraction problems in medical user-generated content, such as word importance and word stickiness features.
@@
 
-In our work, we use the same approach as Cao \cite{cao2010automatically} which treats keyphrase extraction as a sequence labeling task.
-In our experiment, we employed and combined various deep learning architectures, such as convolutional neural networks and bi-directional long short-term memory networks, to exploit high level features between neighboring word positions.
+In our work, we use the similar approach as Cao \cite{cao2010automatically} which treats keyphrase extraction as a sequence labeling task.
+The difference is that, in our experiment, we employed and combined various deep learning architectures, such as convolutional neural networks and bi-directional long short-term memory networks, to exploit high level features between neighboring word positions.
 To improve the quality of our model, we leverage several new hand-crafted features that can handle our keyphrase extraction problems in medical user-generated content, such as word importance and word stickiness features.
@@
 For the unsupervised line of research, keyphrase extraction is formulated as a ranking problem, in which each candidate keyphrase is assigned a score that represents its keywordness value.
-The well known researches in unsupervised approach are \cite{rake} which use the ratio of word degree and frequency to rank terms.
-\cite{mihalcea2004textrank} developed a graph based approach which treats words as vertices and construct edges between words using co-occurrence.
+The well known research in unsupervised approach is RAKE \cite{rake}, which use the ratio of word degree and frequency to rank terms.
+Mihalcea and Tarau \cite{mihalcea2004textrank} developed a graph based approach which treats words as vertices and construct edges between words using co-occurrence.
 

### 2017-05-24 (old)paper-content.tex
Masukin Ablation tp jadi kebanyakan hiks

--- 2017-05-24 paper-content.tex
@@
 thanks before)}
+
 It can be seen on the example that keyphrases can be a word, phrase, or even clause.
-Furthermore, there are many grammatical errors and abbreviation, such as \texttt{sy} for the replacement of the word \texttt{saya (I)}.
-It is also worth to note that keyphrase \texttt{diet mayo (mayo diet)} is not part of medical entity listed by Wahid \cite{skripsiWahid} and Abid \cite{skripsiKakAbid} research.
+Furthermore, there are many grammatical errors and abbreviation, such as \texttt{"sy"} for the replacement of the word \texttt{"saya (I)"}.
+It is also worth to note that keyphrase \texttt{"diet mayo (mayo diet)"} is not part of medical entity categories listed by Wahid \cite{skripsiWahid} and Abid \cite{skripsiKakAbid} research.
 Thus, extracting keyphrase for getting patient needs is not a trivial task.
@@
 In addition, we also propose word stickiness feature to make our model constructs keyphrases
-%===========Unused Introduction========================
 
-\iffalse
-Keyphrases are usually selected phrases or clauses that can capture the main topic of a given document \cite{turney2000learning}.
-They can provide readers with highly valuable and representative information, such that looking at keyphrases is sufficient to understand the whole body of document.
-Moreover, keyphrases are important for text summarization, document clustering, and classification task (\cite{classDocumentEkp1}; \cite{qaEkp}; \cite{gong2009improving}).
-Previous works have shown that using keyphrases to generate queries can improve the quality of question retrieval in medical question answering forum \cite{cao2010automatically}.
-
-Keyphrase extraction methods have been mostly using statistical approach (\cite{sparck1972statistical} \cite{zhang2007comparative} \cite{rake} \cite{mihalcea2004textrank}) and supervised learning approach (\cite{witten1999kea} \cite{medelyan2009human} \cite{marujoMAUI}).
-The statistical approach often involves keyword candidate selection and candidate's property calculation.
-The "keywordness" value of a candidate phrase is usually scored based on its typical length as well as frequency in which document it appears \cite{rake}.
-While the statistical approach is very efficient to generate keyphrases, our experiments showed that it performs poorly on user generated contents and short documents.
-The other approach is based on supervised learning, there are two common approach in supervised learning: classification and sequence labeling.
-In classification approach, candidate keyphrases are extracted using statistical \cite{sparck1972statistical} or language model \cite{ekpNeuralNetworks}.
-Then, the candidate keyphrases are classified whether a candidate is a keyphrase or not by using a pre-trained model.
-However, classification approach cannot capture semantic relationship between words in a document \cite{surveyPopulerTerbaruEkp}.
-In sequence labeling approach,  like the one proposed by \cite{cao2010automatically} and \cite{zhang2008automatic}.
-They define keyphrase extraction task as a sequence labeling task, in which each word in the document can have two possible labels: keyword or non-keyword.
-The method they proposed worked well by outperforming unsupervised approach.
-However, synonym and ambiguity words cannot be handled properly \cite{zhang2008automatic}.
-For example, we give a medical question asked by a patient in Indonesian language:
-	\textit{\\Dok , saya sering sekali merasa \textbf{\emph{kram pada perut kanan bagian atas}} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}.
-Dan saat kambuh seperti itu, \textbf{nafas sangat sakit}.
-Seminggu yang lalu sampai terkapar karena tidak kuat menahan sakitnya saat bernafas.
-apakah ada hubungannya dengan \textbf{diet mayo}?
-terima kasih sblumnya dok.}
-	\texttt{(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}.
-And when the symptom occur it's \textbf{very hurt when breathing}.
-Last week i fainted because cannot hold the pain when i was breathing.
-is there any connection with \textbf{moyo diet}?
-thanks before)}
-
-It can be seen on the example that keyphrases can be a word,
-phrase, or even clause. Furthermore, there are many grammatical
-errors and abbreviation, such as sy for the replacement of the word
-saya (I). It is also worth to note that keyphrase diet mayo (mayo
-diet) is not part of medical entity listed by Wahid [9] and Abid
-[4] research. Thus, extracting keyphrase for getting patient needs
-is not a trivial task.
-
-In our work, we use the same approach as Cao \cite{cao2010automatically} which treats keyphrase extraction as a sequence labeling task.
-In our experiment, we employed and combined various deep learning architectures, such as convolutional neural networks and bi-directional long short-term memory networks, to exploit high level features between neighboring word positions.
-To improve the quality of our model, we leverage several new hand-crafted features that can handle our keyphrase extraction problems in medical user-generated content, such as word importance and word stickiness features.
-The word importance feature is enable to rank words in a document by their importance value.
-The more important a word is to the content of document, the higher its "keywordness" value would seem to be.
-In addition, we also propose word stickiness feature to make our model constructs keyphrases better.
-
-We also employed pre-trained word embedding to incorporate contextual, semantic, and syntactic information of a word.
-For example, we found that pre-trained word embedding can handle slang words and abbreviations by giving their word vectors closer to the vectors of their canonical forms.
-Finally, to evaluate the effectiveness of our model, we collected and manually annotated data from Indonesian medical forum questions, such as alodokter, health detik, doktergratis, dokter.id, doktersehat, klikdokter \footnote{www.alodokter.com, health.detik.com, www.dokter.id, www.doktersehat.com, www.klikdokter.com}.
-After that, the dataset was used for both training and testing our computational models.
-For our baseline, we use RAKE  \cite{rake}, which is the current state of the art model for extracting keyphrases.
-
-This paper is organized as follows.
-In section 2 we discuss related works in keyphrase extraction.
-In section 3, the proposed keyphrase extraction method has been discussed.
-We present the evaluation and the experimental results in section 4.
-\fi
-%====================================================
 \section{Related Works}
@@
 The well-known research in unsupervised approach are RAKE \cite{rake} which use the ratio of word degree and frequency to rank terms.
-Mihalcea and Tarau \cite{mihalcea2004textrank} developed a graph-based approach which treats words as vertices and constructs edge between words using co-occurrence.
+There is also Mihalcea and Tarau \cite{mihalcea2004textrank} who developed a graph-based approach which treats words as vertices and constructs edge between words using co-occurrence.
 
@@
 
-%=============================Unused Related Works=======
-\iffalse
-In general, keyphrase extraction methods can be divided into two groups: unsupervised ranking (statistical) approach and supervised machine learning approach.
-For the unsupervised line of research, keyphrase extraction is formulated as a ranking problem, in which each candidate keyphrase is assigned a score that represents its keywordness value.
-Furthermore, this kind of approach does not require training data, which is often very difficult to obtain.
-On the other hand, supervised machine learning approach requires training data that contains a collection of documents with their labeled keywords.
-Using this approach, keyphrase extraction is usually treated as a classification or sequence labeling task in the level of words or phrases.
-The first step of this approach generates candidate keyphrases from a particular document.
-Finally, every candidate keyphrase in the document will be classified as either a keyphrase or non-keyphrase.
-Recently, a well-known supervised approach for keyphrase extraction is based on sequence labeling problem (\cite{zhang2008automatic}\cite{cao2010automatically}\cite{zhang2016keyphrase}).
-The assumption behind this model is that the decision on whether a particular word serves as a keyword is affected by the information from its neighboring word positions.
-
-In the work of \cite{sparck1972statistical}, they leverage TF-IDF to get the most significant words.
-Specifically, they utilize term frequency and the inverse of document frequency to rank terms in the document.
-First, this Rapid Automatic Keywords Extraction \cite{rake} uses stopwords to split a document into several candidate keyphrases.
-All candidates will be ranked by the degrees and frequencies of all words inside them.
-Finally, the rank points of each candidate is obtained by summing over all degrees and frequencies of all words contained in each keyphrase.
-RAKE is proven to be successful for extracting keyphrases in special documents such as paper and article \cite{rake}.
-
-There is also a popular graph-based approach, namely TextRank \cite{mihalcea2004textrank}, i.e., a modified PageRank algorithm to extract keyphrases from a document.
-They exploit word co-occurrence information to build a document graph, in which a word serves as a node and co-occurence information determines an edge between two nodes (words).
-After they build the graph, they actually run PageRank algorithm to determine the keywordness score for each node in the graph.
-A word with high PageRank value denotes that its related concept can be found in many location inside the document, which means that it is a good candidate for keyword.
-After that, keyphrases can be obtained using post-processing step that may combine contiguous candidates into one keyphrase.
-
-One of the earlier supervised approaches in the problem of keyphrase extraction is KEA \cite{witten1999kea}.
-KEA uses tf-idf and first occurrence of the term to identify candidate keyphrases.
-They use a machine-learning algorithm (i.e., Naive Bayes) to predict whether or not a candidate is a good keyphrase.
-\cite{medelyan2009human} developed a system called MAUI that can extract keyphrases using trained corpus and controlled vocabulary.
-MAUI itself is an improvement to the aforementioned supervised model, KEA.
-Furthermore, Marujo et al., \cite{marujoMAUI} use word embedding and brown clustering as features.
-Their experiment result had shown that the proposed features and MAUI performs better than statistical methods, such as simple tf-idf approach.
-
-The utilization of neural networks is also quite popular in the recent years.
-Sarkar and Kamal \cite{ekpNeuralNetworks} use Feed Forward Neural Networks to classify candidate keyphrases.
-To extract candidate keyphrases, they use POS tag information for classifying all words in the document.
-Then, Deterministic Finite Automation (DFA) is used to extract noun phrases as candidate keyphrases.
-Furthermore, deep neural networks is also employed for extracting keyphrase, like the one proposed by Zhang et al., \cite{zhang2016keyphrase}, that uses joint Recurrent Neural Networks (RNNs) layer to capture keyphrase sequences in microblogs.
-The research had shown that RNN is very effective to extract keyword.
-
-Unfortunately, there are limited works regarding the task of keyphrase extraction in medical domain.
-\cite{ekpMedicalDocumentHybrid} use a hybrid medical knowledge base and statistical approach to extract keyphrases from medical articles.
-They use stopwords to split candidate keyphrases, then candidates are ranked with two aspects: PF-IDF (Phrase Frequency * Inverse Document Frequency) and domain knowledge which is extracted from medical article.
-In terms of medical social media content, \cite{cao2010automatically} use Conditional Random Fields (CRFs) for extracting keywords from medical questions in online health-forum.
-They use information, such as word location and length as features in their experiments.
-\fi
-%===============================================
 \section{METHODOLOGY}
-
-\iffalse
-\subsection{DATA AND ANNOTATION}
-To analyze the effectiveness of our model for keyphrase extraction in user-generated medical domain, we constructed an evaluation dataset.
-A number of questions was gathered from Indonesian medical question answering forum.
-The data was crawled by \cite{skripsiKakRadit} and \cite{skripsiWahid} in their experiment.
-Generally, we gathered 416 question-answer pairs from \cite{skripsiKakRadit} and \cite{skripsiWahid}.
-We decided to use the same question-answers pairs to observe our keyphrases and medical entities that has been annotated by them.
-In addition, system for recognizing medical entities is not fully build, by using the same document we can use the annotated medical entities as our feature.
-
-From analyzing these question-answer pairs, we found some noise and unnecessary information.
-Question and answer have different main topic and focus.
-Moreover, we are focusing our task for getting user intentions and needs in our experiment.
-Based on that problem, we only use questions by users and remove answers by the doctors because it would be a better representation of user intentions and needs.
-There is also unnecessary information such as URL and email.
-We replace URL with "URL"  and email with "email" since we were focusing on textual content.
-Moreover, we also removed ads and spam in the data we gathered.
-
-Because we want to process all the questions by users, we tokenize every question in our data.
-The tokenization process included separating alphanumeric with non-alphanumeric.
-Then separating alphanumeric with numeric.
-
-To evaluate the quality of our model.
-We manually annotated or data to label keyphrases in 416 questions.
-In this work, we use "IOB" tagging scheme to label every word \cite{collobert2011natural}.
-In Table X, we give an example sequence with labels for each word.
-The statistical information of the dataset can be seen in Table
-\fi
-
 In this work, we view keyphrase extraction problem as a sequence labeling task.
@@
 As a result, we leveraged nine handcrafted features that can help our model to characterize the sequence of keyphrases.
-Formally, our feature functions are, $f_1, f_2, ..., f_9$, which map a word to a particular feature value.
 
@@
 The word embeddings we used in this work were trained using a document that we gathered from Indonesia online forum, medical article, and medical question answering forum.
-Thus, the feature value for the word \texttt{headache} is $f_1(headache) = [v_1, v_2, ..., v_n]$ where $v_i$ is a real value and $n$ is 128.
 
-\textbf{Medical Dictionary.} In our experiment, we leveraged a medical knowledge base feature using a medical dictionary.
+\textbf{Medical Dictionary.} In our experiment, we leverage a medical knowledge base feature using a medical dictionary.
 Our medical dictionary contains a list of symptom, disease, treatment, and drug in the Indonesian language.
@@
 Based on this feature, we classified words by their appearance in the medical dictionary.
-The dictionary was built by combining three dictionaries from \cite{skripsiKakAbid} research.
+The dictionary was built by combining disease, symptom, treatment, and drug dictionaries from \cite{skripsiKakAbid} research.
 The original dictionaries contained disease, symptom, treatment, and drug separately in each dictionary.
-For example, $f_2(headache) = [0, 1]$ because \texttt{headache} is disease and inside the dictionary.
+We represent this feature as one-hot-vector.
 
 \textbf{Word Length.} This feature represents the length of each word (i.e., the number of characters in every word).
-This feature is based on \cite{cao2010automatically} research on keyphrase extraction in medical question who added word length as a feature because domain-specific words (e.g.
-"tuberculosis") tend to be lengthy when compared to common English words, and there is a correlation between the length of a word and its IDF value \citep{cao2010automatically}.
-Thus we use the same feature for Indonesian language.
-For example, $f_3(headache) = [8]$
+This feature is based on Cao et al.
+\cite{cao2010automatically} research on keyphrase extraction in medical question who added word length as a feature because domain-specific words (e.g.
+"tuberculosis") tend to be lengthy when compared to common English words, and there is a correlation between the length of a word and its IDF value \cite{cao2010automatically}.
 
-\textbf{Word Position.} We also adapted word position as feature based on \cite{cao2010automatically}research.
+\textbf{Word Position.} We also adapted word position as feature based on Cao et al.
+\cite{cao2010automatically} research.
 Based on their observation, an important term sometimes appears toward the end of a clinical question.
 For example, "medicine for bell's palsy" appear towards the end of a question "what is the best medicine for bell's palsy?".
-Thus, the value of the word \texttt{palsy} is $f_4(palsy) = [8]$ because it is on the first position of the sentence.
 
@@
 We represent our POS tag feature as one-hot-vector.
-For example, the word \texttt{cancer} has noun tag, $f_5(cancer) = [0, ..,1, ...0]$.
 
@@
 We also use one-hot-vector to represent this feature.
-For example, $f_6(cancer) = [0, 0, 0 ,1]$
 
 \textbf{Abbreviation and Acronym.} We also identified words by their appearance in abbreviation or acronym dictionary gathered by \cite{skripsiKakAbid}.
-We observed that important word may not be shortened by the users, such as "cancer", "flu", "bell’s palsy".
+We observed that important word may not be shortened by the users, such as "cancer", "flu", "bell's palsy".
 One-hot-vector is used to classify whether a word is an abbreviation/acronym or not.
 For example, the word \texttt{mengapa (why)} sometimes is abbreviated into \texttt{mngp} by some patients.
-Thus, $f_7(mngp) = [0, 1]$
 
@@
 \end{equation}
-For example, $f_6(cancer) = [0.56]$.
+
 \textbf{Word Stickiness.} As a keyphrase, a sequence must be in a valid order.
@@
 \begin{equation}\label{eq:pmi}
-PMI(x,y)=log(\frac{p(x, y)}{p(x)*p(y)})
+PMI(x,y)=log(\frac{P(x, y)}{P(x).P(y)})
 \end{equation}
-For example, the word \texttt{cancer} in sentence "How to prevent cancer doc ?", the feature value is $f_6(cancer) = [0.56, 0.1]$.
-It is worth ti note that the word \texttt{cancer} is rarely co-occur with the word \texttt{doc}.
+For example, the word \texttt{cancer} in sentence "How to prevent cancer doc ?", the feature value is $f_s(cancer) = [0.56, 0.1]$ where $f_s$ is feature stickiness feature function.
+It is worth to note that the word \texttt{cancer} is rarely co-occur with the word \texttt{doc}.
 
@@
 
-We also experimented on customizing the way we input the features underneath our aforementioned networks.
-Instead of concatenating all features into one vector, we tried to give weight for every feature we have.
+We also experimented on customizing the way we input the features underneath our aforementioned model.
+Instead of concatenating all features into one vector, which can be seen in Formula \ref{eq:concat}, we tried to give weight for every feature we have.
+\begin{equation}\label{eq:concat}
+Z =  concatenate(F_{1}, F_{2}, ..F_{9})
+\end{equation}
 We argue that each feature has different contribution to the model.
@@
 \begin{equation}
-Z =  tanh(W _{1}*F_{1} + W_{2}*F_{2} + .. + W_{n}*F_{n})
+Z =  tanh(W _{1}.F_{1} + W_{2}.F_{2} + .. + W_{n}.F_{9})
 \end{equation}
-Where $W_{i}$ are the weight for each feature and $F_{i}$ are the extracted feature in vector form.
+
+Where $Z$ is the input representation,  $W_{i}$ are the weight for each feature, and $F_{i}$ are the extracted feature in vector form.
 
@@
 \subsection{Evaluation}
-One of the evaluation that we use in our work is using partial evaluation.
+For our experiments, we employed 10-cross-validation on our dataset.
+Evaluation method that we use in our work is using partial evaluation to get precision, recall, F1-measure for evaluation metrics.
 This evaluation is used because we treat keyphrases as sequences of words.
@@
 
-We use Recall, Precision, and F1 score as our evaluation parameters.
-Recall shows the number of correctly predicted keyphrases divided by the the total number of assigned keyphrases and Precision is the number of correctly predicted keyphrase divided by the total number of predicted keyphrases.
-To calculate F1 score we use Recall and Precision as parameters which is 2  Recall  Precision/ (Recall + Precision).
-%===========Commented Feature Ablation Study
-\iffalse
-\subsection{Feature Ablation Study}
-In this part, perform a feature ablation study.
-By considering all the features, and then removing one of these features, we want to estimate the importance of the features.
-To the experiment.
-We use 80\% as training set, and 20\% as a testing set.
-We used precision (P), recall (R), and F1-score (F1) as evaluation metrics.
-Table \ref{tab:ablation} show the experimental result.
-Then, we use LSTM as evaluation model because it is the most simple architecture.
-These are the following features we proposed: word stickiness (Ws), word abbreviation and acronym (Wa), Medical Entities (Me), Word Location (Wp), Word Length (Wl), Word Importance (Wi), POS tag (Pt), Medical Dictionary (Md).
-
-\begin{table*}
-	\caption{Feature Ablation Study Result}
-	\label{tab:ablation}
-	\begin{tabular}{lccc}
-		\toprule
-		Features&Precision&Recall&F-Measure\\
-		\midrule
-		We + Ws + Wa + Me + Wp + Wl + Wi + Pt + Md & \textbf{84.01\%} & 75.79\% & \textbf{79.69\%} \\
-
-		Ws + Wa + Me + Wp + Wl + Wi + Pt + Md & 79.93\% & 57.45\% & 66.85\% \\
-
-		We + Wa + Me + Wp + Wl + Wi + Pt + Md & 76.39\% & 73.59\% & 74.96\% \\
-
-		We + Ws + Me + Wp + Wl + Wi + Pt + Md & 78.44\% & 73.83\% & 76.07\% \\
-
-		We + Ws + Wa + Wp + Wl + Wi + Pt + Md & 79.38\% & 76.28\% & 77.8\% \\
-
-		We + Ws + Wa + Me + Wl + Wi + Pt + Md & 74.24\% & \textbf{78.23\%} & 76.19\% \\
-
-		We + Ws + Wa + Me + Wp + Wi + Pt + Md & 75.36\% & 76.28\% & 75.82\% \\
-
-		We + Ws + Wa + Me + Wp + Wl + Pt + Md & 83.69\% & 75.3\% & 79.27\% \\
-
-		We + Ws + Wa + Me + Wp + Wl + Wi + Md & 79.68\% & 74.81\% & 77.17\% \\
-
-		We + Ws + Wa + Me + Wp + Wl + Wi + Pt & 75.66\% & 76.03\% & 75.85\% \\
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-The experimental results in Table \ref{tab:ablation} shows that every feature has a positive contribution to the model.
-It is shown by iteratively remove each feature one by one and every time we remove a feature, F-1 score always dropped.
-Hence, we use every feature to train our model in the next experiments.
-\fi
-%================================================================
 \subsection{Results}
@@
 \end{table}
-We created a scenario to evaluate the performance of our model.
-In this scenario, we also compared our model to an unsupervised learning algorithm using RAKE \cite{rake} and a supervised learning algorithm CRF task.
+
+For comparison, we implemented RAKE \cite{rake} and CRF \cite{zhang2008automatic}, which use unsupervised and supervised approach.
+For CRF, we use the same features proposed above.
 We also conducted an experiment to proof the effectiveness of our CNN layer by comparing standard B-LSTM and B-LSTM with CNNs layer(CNN-B-LSTM).
@@
 
-For comparison, we implemented RAKE \cite{rake} and CRF \cite{zhang2008automatic}, which use unsupervised and supervised approach. For CRF, we use the same features proposed above.
-
 As we can see in Table \ref{tab:model_scenario}, RAKE and CRF underperformed on Indonesian user-generated medical question since RAKE were specially devised for formal text.
-By our observation of the result provided by CRF, the method failed to predict long sequences as a keyphrase.
+For CRF, our observation from the result provided by CRF, the method failed to predict long sequences as a keyphrase.
 
@@
 However, our weighting layer failed to provide some improvement.
-We argue that weighting layer has a significant information loss when converting features vector.
 
@@
 Some of the error are uncompleted keyphrases.
-For example "headache on (sakit kepala pada)", "medicine for (obat untuk)".
+For example "headache on (pusing pada)", "medicine for (obat untuk)".
 Our model also failed to capture complex medicine name and disease.
@@
 We have proposed a model to address the task of keyphrase extraction on Indonesian user-generated medical domain.
-Extracting information patient intentions and needs on user-generated medical content is not a trivial task due to the fact that the content is usually short, contain many medical terms, and written in an unstructured format, as opposed to formal text.
+Extracting information patient intentions and needs on user-generated medical contents is not a trivial task due to the fact that the content is usually short, contain many medical terms, and written in an unstructured format, as opposed to formal text.
 Our model is based on sequence labeling task that employs deep learning approach using convolutional neural networks and bi-directional lstm.
@@
 Although our model outperforms state of the art methods for keyphrase extraction, further improvements are needed especially in evaluation method which cannot cover the whole problem.
-\iffalse
-We investigate a keyphrase extraction problem especially in Indonesian medical questions domain with sequence labeling approach.
-We leverage a deep learning approach using CNNsand B-LSTM.
-Moreover, we also extracted nine features that capture medical concepts from a knowledge base, and linguistic components as our features.
-With this model and features, we are able to overcome problems such as informal language, short document, and medical domain specific.
-Our model achieves F1 score of 82.41\% on manually annotated Indonesian medical questions.
-
-For handling several problems that occurred in this experiment, we suggest to create a language model for post-processing.
-The language model expected to handle cases like uncompleted keyphrase or connection between keyphrase.
-
-Furthermore, we realized that there are no solid evaluation method for keyphrase extraction.
-Partial evaluation may handle how the model extract sequences in a document.
-However, weights for importance in sequences are different between words.
-For example "therapy for pregnancy", in that keyphrase we may realize that "pregnancy" is more important than other words.
-Thus partial evaluation failed to capture that problem.
-\fi

### 2017-05-24 paper.tex
Masukin Ablation tp jadi kebanyakan hiks

@@
 %
-\iffalse
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>  
-\end{CCSXML}
-
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
-\fi
 
@@
 
-\input{paper-content}
+\section{Introduction}
+Health-related or question-answering forum is becoming a trend today.
+With those forum, seeking health information and asking questions to doctors is pretty much easier.
+As a result, there is a growing need for enriching medical-related knowledge, for which it can be very valuable for several tasks in IR and NLP \cite{cao2010automatically}.
+However, understanding those various health-related contents, especially from an online forum, is simply not a trivial task since they are written in free text format (i.e.
+unstructured format), and often prone to grammatical and typographical glitches.
+Therefore, reducing the complex characteristics of the textual contents, including but not limited to linguistic variations, into structured information could be very beneficial for the text interpretation process.
+
+One possible solution is harnessing medical entity recognizer to extract medical terms that represent the document they belong.
+However, we argue that there are many missing pieces of information when we merely rely on medical entities or terminologies as our main information for representing a particular document.
+Hence, we leverage keyphrase to cover more valuable information.
+Keyphrases are usually selected phrases or clauses that can capture the main topic of a given document \cite{turney2000learning}.
+They can provide readers with highly valuable and representative information, such that looking at keyphrases is sufficient to understand the whole body of a document.
+
+In this paper, we only focus the task of keyphrase extraction on Indonesian medical questions from online forums, such as alodokter\footnote{www.alodokter.com}, health detik \footnote{health.detik.com}, dokter.id \footnote{www.dokter.id}, klikdokter \footnote{www.klikdokter.com}.
+We present a new keyphrase extraction techniques to extract more important information about the patient intentions and needs, which expressed inside Indonesian medical questions.
+Furthermore, we also propose a new definition of keyphrases, which is based on our observation of health-related and user-generated questions.
+Actually, our final goal is to develop medical question answering systems to assist physicians or people obtaining health information.
+The work presented in this paper is absolutely in line with our goal since important keyphrases of a medical question can be used to formulate a query for the passage or question retrieval subsystem \cite{gong2009improving}.
+The following example shows the results of keyphrase extraction in a medical document:
+	\textit{\\Dok , saya sering sekali merasa \textbf{\emph{kram pada perut kanan bagian atas}} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}.
+Dan saat kambuh seperti itu, \textbf{nafas sangat sakit}.
+apakah ada hubungannya dengan \textbf{diet mayo}?
+terima kasih sblumnya dok.}
+	\texttt{(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}.
+And when the symptom occur it's \textbf{very hurt when breathing}.
+is there any connection with \textbf{moyo diet}?
+thanks before)}
+
+It can be seen on the example that keyphrases can be a word, phrase, or even clause.
+Furthermore, there are many grammatical errors and abbreviation, such as \texttt{"sy"} for the replacement of the word \texttt{"saya (I)"}.
+It is also worth to note that keyphrase \texttt{"diet mayo (mayo diet)"} is not part of medical entity categories listed by Wahid \cite{skripsiWahid} and Abid \cite{skripsiKakAbid} research.
+Thus, extracting keyphrase for getting patient needs is not a trivial task.
+
+In our work, we use similar approach as in Cao et al.
+\cite{cao2010automatically}, which treats keyphrase extraction as a sequence labeling task.
+The difference is that, in our experiment, we employed and combined various deep learning architectures, such as convolutional neural networks and bi-directional long short-term memory networks, to exploit high level features between neighboring word positions.
+To improve the quality of our model, we leverage several new hand-crafted features that can handle our keyphrase extraction problems in medical user-generated content, such as word importance and word stickiness features.
+The word importance feature is enable to rank words in a document by their importance value.
+The more important a word is to the content of document, the higher its "keywordness" value would seem to be.
+In addition, we also propose word stickiness feature to make our model constructs keyphrases
+
+\section{Related Works}
+In general, keyphrase extraction methods can be divided into two groups: unsupervised ranking (statistical) approach and supervised machine learning approach.
+For the unsupervised line of research, keyphrase extraction is formulated as a ranking problem, in which each candidate keyphrase is assigned a score that represents its keywordness value.
+The well-known research in unsupervised approach are RAKE \cite{rake} which use the ratio of word degree and frequency to rank terms.
+There is also Mihalcea and Tarau \cite{mihalcea2004textrank} who developed a graph-based approach which treats words as vertices and constructs edge between words using co-occurrence.
+
+On the other hand, supervised machine learning approach requires training data that contains a collection of documents with their labeled keywords which is often very difficult to obtain.
+Using this approach, keyphrase extraction is usually treated as a classification or sequence labeling task in the level of words or phrases.
+The first step of this approach generates candidate keyphrases from a particular document.
+Finally, every candidate keyphrase in the document will be classified as either a keyphrase or non-keyphrase.
+The well-known method for this approach is KEA \cite{witten1999kea}, they use machine-learning (i.e., Naive Bayes) for classifying candidate keyphrases.
+The utilization of neural networks in classifying candidate keyphrases also conducted by \cite{ekpNeuralNetworks}.
+Recently, a well-known supervised approach for keyphrase extraction is based on sequence labeling problem (\cite{zhang2008automatic}, \cite{cao2010automatically}, \cite{zhang2016keyphrase}).
+The assumption behind this model is that the decision on whether a particular word serves as a keyword is affected by the information from its neighboring word positions.
+
+For medical document, Sarkar and Kamal \cite{ekpMedicalDocumentHybrid} use a hybrid medical knowledge base and statistical approach to extract keyphrases from medical articles.
+They use stopwords to split candidate keyphrases, then candidates are ranked with two aspects: PF-IDF (Phrase Frequency * Inverse Document Frequency) and domain knowledge which is extracted from medical article.
+
+Unfortunately, there are limited works regarding the task of keyphrase extraction from user generated on medical question, especially in Indonesian language.
+Similar research in English language has been conducted by Cao et al.
+\cite{cao2010automatically} use Conditional Random Fields (CRFs) for extracting keywords from medical questions in online health forum.
+They use information, such as word location and length as features in their experiments.
+
+\section{METHODOLOGY}
+In this work, we view keyphrase extraction problem as a sequence labeling task.
+That is, given a medical question containing $N$ words $w = (w_1, w_2,...,w_N)$, we want to find the best sequence of labels $y = (y_1, y_2,..., y_N)$, in which each label is determined using probabilities $P(y_i|w_{i-l},...,w_{i+l},y_{i-l},...,y_{i+l})$ where $l$ is a small number.
+
+Because we have a small dataset, our model would have a small learning material and an end-to-end learning approach will not work well.
+As a result, we leveraged nine handcrafted features that can help our model to characterize the sequence of keyphrases.
+
+\textbf{Word Embedding (We).} In the experiments, we use word embedding as input to the neural network.
+A skip-gram model from Mikolov \cite{mikolov2013wordembed} research was used to generate these 128-dimensional vectors for documents in evaluation data.
+The dimension of the vector was chosen based on \cite{skripsiWahid} experiment.
+The word embedding we used in this work were trained using a document that we gathered from Indonesia online forum, medical article, and medical question answering forum.
+With this feature, slank words can be handled better.
+
+\textbf{Medical Dictionary (Md).} In our experiment, we leverage a medical knowledge base feature using a medical dictionary.
+The dictionary was built by combining disease, symptom, treatment, and drug dictionaries from \cite{skripsiKakAbid} research.
+The rationale behind this feature is intentions and needs of patients is more focused on their disease, symptom, treatment, and drug.
+Based on this feature, we classified words by their appearance in the medical dictionary.
+We represent this feature as one-hot-vector.
+
+\textbf{Word Length (Wl).} This feature represents the length of each word (i.e., the number of characters in every word).
+This feature is based on Cao et al.
+\cite{cao2010automatically} research on keyphrase extraction in medical question.
+This feature is added because domain-specific words (e.g.
+"tuberculosis") tend to be lengthy when compared to common English words, and there is a correlation between the length of a word and its IDF value \cite{cao2010automatically}.
+
+\textbf{Word Position (Wp).} We also adapted word position as feature based on Cao et al.
+\cite{cao2010automatically} research.
+Based on their observation, an important term sometimes appears toward the end of a clinical question.
+For example, "medicine for bell's palsy" appear towards the end of a question "what is the best medicine for bell's palsy?".
+
+\textbf{POS-tag (Pt).} POS-tag of words was also added as our feature.
+POS-tag may give model grammatical information and a better understanding of ambiguous words.
+By our observation, many keyphrases have a common POS pattern.
+We use Stanford Part-Of-Speech Tagger and a model which pre-trained by Dinakaramani \cite{dinakaramani2014designing}.
+We represent our POS tag feature as one-hot-vector.
+
+\textbf{Medical Entity (Me).} We use medical entity which was annotated by Wahid \cite{skripsiWahid} using four categories: drug, treatment, symptom, disease.
+By our observation, medical entities are sometimes part of keyphrases.
+Furthermore, medical entities can provide more information about drug or disease which not available in training data or a medical dictionary.
+We also use one-hot-vector to represent this feature.
+
+\textbf{Abbreviation and Acronym (Wa).} We also identified words by their appearance in abbreviation or acronym dictionary gathered by Abid \cite{skripsiKakAbid}.
+We observed that important word may not be shortened by the users, such as "cancer", "flu", "bell's palsy".
+One-hot-vector is used to classify whether a word is an abbreviation/acronym or not.
+For example, the word "\textit{mengapa (why)}" sometimes is abbreviated to \texttt{mngp} by some patients.
+
+\textbf{Word Importance (Wi).} The purpose of this feature is to rank words in a document by their importance.
+To extract this feature, we adapted  TextRank \cite{mihalcea2004textrank} algorithm for ranking words in a document.
+They represent words as vertices in the graph and the distance between words as edges.
+However, in building an undirected graph, we use a word similarity as a weight for edges by using our pre-trained word embedding model to calculate cosine similarity between two word vectors.
+Two words have a connected edge if their similarity is not negative.
+Moreover, we use a modified PageRank \cite{page1999pagerank} algorithm that consider edges weight in the calculation.
+Formally, let $G = (V, E)$ be an undirected graph with the set of vertices V and set of edges E, where E is a subset of $V \times V$.
+For a given vertex $V_i$ let $In(V_i)$ be the set of vertices that point to it (predecessors) and let $Out(V_i)$ be the set of vertices that vertex $V_i$ points to (successors).
+The modified PageRank formula that proposed by \cite{mihalcea2004textrank} can be seen in Formula \ref{eq:pagerank}.
+\begin{equation}\label{eq:pagerank}
+WS(V_{i})=(1-d) + d * \sum_{V_{i} \in In(V_{i})} \frac{w_{ji}}{\sum_{V_{i} \in Out(V_{j})}}w_{jk}
+\end{equation}
+
+\textbf{Word Stickiness (Ws).} As a keyphrase, a sequence must be in a valid order.
+There is some noise such as misuse punctuation by users.
+For example, "\textit{Saya mengalami pusing pada jidat sakit perut dan pandangan kabur} (I am having a headache on forehead stomachache and blurred vision)", there is no comma between "jidat (forehead)", "sakit perut (stomachache)" and "dan (and)".
+Our model may mistake the sequence "(jidat sakit perut)forehead stomachache" as a keyphrase.
+Based on that problem, we propose a feature that may capture how likely of a given word is occurred together with the word before and after.
+We use Pointwise Mutual Information (PMI) of a bigram probability to capture the likeness.
+Formula \ref{eq:pmi} is the formula for calculating the PMI value.
+In that formula, $p(x)$ is the occurrence probability of word $x$, $p(y)$ is the occurrence probability of word $y$, and $p(x, y)$ is the probability of word $x$ and $y$ co-occur together.
+\begin{equation}\label{eq:pmi}
+PMI(x,y)=log(\frac{P(x, y)}{P(x).P(y)})
+\end{equation}
+The feature function is formally described as $f_s(w) = [x, y]$ where $w$ is a word, x is the stickiness value between w and the word before, and y is the stickiness value between w and the word before.
+For example, the word "\texttt{cancer}" in sentence "\texttt{How to prevent cancer doc?}", the feature value is $f_s(cancer) = [0.56, 0.1]$ where $f_s$ is feature stickiness feature function.
+It is worth to note that the word "\texttt{cancer}" is rarely co-occur with the word "\texttt{doc}".
+Therefore, the stickiness value between the word "cancer" and "doc" is relatively smaller than "prevent".
+
+We process the sequences word by word.
+All Features are extracted and concatenated into one vector from every word as the input representation of the model.
+The output of our model are labels which describe whether a word is either part of keyphrase or not.
+
+We introduce Convolutional Neural Networks (CNNs) to exploit high-level features between neighboring word positions.
+Based on our observation, a keyphrase is.
+For example, "Doc, I have a frequent back pain.
+What happen?".
+The keyphrase for the previous example is "frequent back pain".
+In order to know that "back" is part of keyphrase, we need information from the word "frequent" which give an intensity of a symptom and "pain" which refer to "back pain" as the main term.
+With CNNs, we argue that our model can capture the surrounding information of a word.
+The output of the CNNs layer will be fed into our next layer which is B-LSTM.
+
+To get a better inference, information from the past and future of sequences can be integrated.
+This approach is proven effective in sequence labeling task such as semantic role labeling \cite{SMRzhou2015end} and named entity recognition \cite{ma2016end}.
+Therefore, we utilized bi-directional LSTM (B-LSTM) for extracting structural knowledge by processing sequences both forward and backward.
+We concatenate the output from both LSTM.
+We build up to two layers of B-LSTM.
+
+Finally, the locally normalized distribution over output labels is computed via a softmax layer.
+
+We also experimented on customizing the way we input the features underneath our aforementioned model.
+Instead of concatenating all features into one vector, which can be seen in Formula \ref{eq:concat}, we tried to give some kind of weighting for every feature we have.
+\begin{equation}\label{eq:concat}
+Z =  concatenate(F_{1}, F_{2}, ..F_{9})
+\end{equation}
+We argue that each feature has different contribution to the model.
+In order to do so, we create a new layer underneath our model to do the weighting scenario.
+Formally, let $Z$ is the input representation and $F_{i}$ are the extracted feature in vector form, $W_i \in {\rm I\!R^{a_i \times b}}$ where the length of $a$ is equal to $F_{i}$ and $b$ is the input representation vector.
+The following equation to weight all features can be seen in below:
+\begin{equation}
+Z =  tanh(W _{1}.F_{1} + W_{2}.F_{2} + .. + W_{n}.F_{9})
+\end{equation}
+
+\section{Evaluations and Results}
+\subsection{Data Collection}
+To develop training data, we collected question-answer pairs which previously crawled by Abid \cite{skripsiKakAbid} and Wahid \cite{skripsiWahid} from Indonesian question-answering medical forum.
+Then, we selected 416 distinct question-answer pairs and removed the answer section for every pair because it is not relevant for obtaining patient intentions and needs.
+Finally, we manually annotated those questions.
+The statistical information of our data can be seen in Table \ref{tab:descriptive_stats}.
+
+\begin{table}
+	\caption{Statistical information of dataset.
+W, K, $\bar{N}_{w}$, $\bar{N}_{k}$ are the total of words, number of keyphrases, average number of words, and average number of keyphrases in each question, respectively.}
+	\label{tab:descriptive_stats}
+	\begin{tabular}{lcccc}
+		\toprule
+		\#questions&W&K&$\bar{N}_{w}$&$\bar{N}_{k}$\\
+		\midrule
+		416 & 26747  & 64.76 & 1861 & 4.49 \\
+
+		\bottomrule
+	\end{tabular}
+\end{table}
+\subsection{Evaluation}
+For our experiments, we employed 10-cross-validation on our dataset.
+We use partial evaluation by Seki et al.
+\cite{seki2003probabilistic} to get precision, recall, F1-measure for evaluation metrics.
+This evaluation is used because we treat keyphrases as sequences of words.
+
+\subsection{Results}
+\begin{table}
+	\caption{Model Scenario Results}
+	\label{tab:model_scenario}
+	\begin{tabular}{lccc}
+		\toprule
+		Models&Precision&Recall&F-Measure\\
+		\midrule
+		RAKE & 43.24\% & 68.19\% & 52.90\% \\
+
+		CRF & 63.44\% & 64.94\% & 62.52\% \\
+		\midrule
+		B-LSTM & 81.88\% & \textbf{83.05\%} & 82.37\% \\
+
+		CNN-B-LSTM & \textbf{82.00\%} & 82.99\% & \textbf{82.41\%} \\
+
+		W-CNN-B-LSTM & 81.08\% & 81.18\% & 81.01\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+For comparison, we implemented RAKE \cite{rake} and CRF \cite{cao2010automatically}, which use unsupervised and supervised approach.
+For CRF, we use the same features proposed above.
+We also conducted an experiment to proof the effectiveness of our CNN layer by comTM with CNNs layer(CNN-B-LSTM).
+Furthermore, we also compared our model with or without weighting layer (W-CNN-B-LSTM).
+
+As we can see in Table \ref{tab:model_scenario}, RAKE and CRF underperformed on Indonesian user-generated medical question since RAKE were specially devised for formal text.
+For CRF, based on our observation from the result provided by CRF, the method failed to predict long sequences as a keyphrase.
+Our CNNs layer also shows improvement in precision and F1 score when compared to standard B-LSTM.
+We suggest that CNNs layer can extract more features implicitly from neighboring words.
+However, our experiment weighting layer failed to provide some improvement.
+
+\subsection{Analysis}
+We performed an analysis to the aforementioned model, the result shown there are several errors.
+Some of the error are uncompleted keyphrases.
+For example, "pusing pada (headache on)", "obat untuk (medicine for)".
+Our model also failed to capture complex medicine name and disease.
+This is due to our small data set and not all medicine and disease are captured in our medical knowledge base or medical entities.
+Moreover, there are also special case that our model failed to handle.
+For example, "penyembuhan untuk sakit kepala dan tenggorokan (treatment for headache and sore throat)", the keyphrase need to be captured as a whole because "sore throat" have a connection with the word "treatment".
+But our model failed to capture that connection and extracted "treatment for headache" and "sore throat" separately instead.
+
+We also ablate our mode by removing our features one by one.
+As we can see in Table \ref{tab:ablation}, F1 score always dropped when we removed one feature.
+Hence, we can say that all of our features are effective for this task.
+ \begin{table}
+	\caption{Average Change in Performance When Removing Each Feature}
+	\label{tab:ablation}
+	\begin{tabular}{cccc}
+		\toprule
+		Removed Features&Precision&Recall&F-Measure\\
+		\midrule
+            We & -4.08 & -18.34 & -12.84 \\
+            Md & -8.35 & +0.24 & -3.84 \\
+            Wl & -8.65 & +0.49 & -3.87 \\
+            Wp & -9.77 & +2.44 & -3.5 \\
+            Pt & -4.33 & -0.98 & -2.52 \\
+            Wa & -5.57 & -1.96 & -3.62 \\
+            Wi & -0.32 & -0.49 & -0.42 \\
+            Me & -4.63 & +0.49 & -1.89 \\
+            Ws & -7.62 & -2.2 & -4.73 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+\section{Conclusion}
+We have proposed a model to address the task of keyphrase extraction on Indonesian user-generated medical domain.
+Extracting information patient intentions and needs on user-generated medical contents is not a trivial task due to the fact that the content is usually short, contain many medical terms, and written in an unstructured format, as opposed to formal text.
+Our model is based on sequence labeling task that employs deep learning approach using convolutional neural networks and bi-directional lstm.
+Several handcrafted features were proposed, including word importance to detect important word in a document and word stickiness for handling unstructured writing.
+Although our model outperforms baseline methods for keyphrase extraction, further improvements are needed.
 

### 2017-05-24 paper.tex
Remove ablation temporary

@@
 Furthermore, there are many grammatical errors and abbreviation, such as \texttt{"sy"} for the replacement of the word \texttt{"saya (I)"}.
-It is also worth to note that keyphrase \texttt{"diet mayo (mayo diet)"} is not part of medical entity categories listed by Wahid \cite{skripsiWahid} and Abid \cite{skripsiKakAbid} research.
+It is also worth to note that keyphrase \texttt{"diet mayo (mayo diet)"} is not part of medical entity categories.
 Thus, extracting keyphrase for getting patient needs is not a trivial task.
@@
 A skip-gram model from Mikolov \cite{mikolov2013wordembed} research was used to generate these 128-dimensional vectors for documents in evaluation data.
-The dimension of the vector was chosen based on \cite{skripsiWahid} experiment.
 The word embedding we used in this work were trained using a document that we gathered from Indonesia online forum, medical article, and medical question answering forum.
@@
 
-\textbf{Medical Entity (Me).} We use medical entity which was annotated by Wahid \cite{skripsiWahid} using four categories: drug, treatment, symptom, disease.
-By our observation, medical entities are sometimes part of keyphrases.
+\textbf{Medical Entity (Me).} We use medical entities which was annotated manually using four categories: drug, treatment, symptom, disease.
+By our observation, medical entity are sometimes part of a keyphrase.
 Furthermore, medical entities can provide more information about drug or disease which not available in training data or a medical dictionary.
@@
 \subsection{Data Collection}
-To develop training data, we collected question-answer pairs which previously crawled by Abid \cite{skripsiKakAbid} and Wahid \cite{skripsiWahid} from Indonesian question-answering medical forum.
-Then, we selected 416 distinct question-answer pairs and removed the answer section for every pair because it is not relevant for obtaining patient intentions and needs.
-Finally, we manually annotated those questions.
+To develop training data, we collected question-answer pairs which previously crawled from Indonesian question-answering medical forum.
+Then, we removed the answer section for every pair because it is not relevant for obtaining patient intentions and needs.
+Finally, we manually annotated 416 questions.
 The statistical information of our data can be seen in Table \ref{tab:descriptive_stats}.
@@
 		\midrule
-		B-LSTM & 81.88\% & \textbf{83.05\%} & 82.37\% \\
+		B-LSTM & 81.88\% & 83.05\% & 82.37\% \\
 
-		CNN-B-LSTM & \textbf{82.00\%} & 82.99\% & \textbf{82.41\%} \\
+		CNN-B-LSTM & 82.00\% & 82.99\% & 82.41\% \\
 
-		W-CNN-B-LSTM & 81.08\% & 81.18\% & 81.01\% \\
+		\textbf{W-CNN-B-LSTM} & \textbf{82.52\%} & \textbf{83.82\%} & \textbf{83.06\%} \\
 		\bottomrule
@@
 We suggest that CNNs layer can extract more features implicitly from neighboring words.
-However, our experiment weighting layer failed to provide some improvement.
+Moreover, our weighting layer shows improvement compared to CNN-B-LSTM.
+Hence, the best result is obtained by W-CNN-LSTM.
 
@@
 But our model failed to capture that connection and extracted "treatment for headache" and "sore throat" separately instead.
-
-We also ablate our mode by removing our features one by one.
+\iffalse
+We also ablate our model by removing our features one by one.
 As we can see in Table \ref{tab:ablation}, F1 score always dropped when we removed one feature.
@@
 \end{table}
+\fi
 \section{Conclusion}
@@
 Our model is based on sequence labeling task that employs deep learning approach using convolutional neural networks and bi-directional lstm.
-Several handcrafted features were proposed, including word importance to detect important word in a document and word stickiness for handling unstructured writing.
+We also proposed a new layer for weighting our features.
+Furthermore, Several handcrafted features were proposed, including word importance to detect important word in a document and word stickiness for handling unstructured writing.
 Although our model outperforms baseline methods for keyphrase extraction, further improvements are needed.

### 2017-05-24 paper.tex
nambah dikit

@@
 Furthermore, there are many grammatical errors and abbreviation, such as \texttt{"sy"} for the replacement of the word \texttt{"saya (I)"}.
-It is also worth to note that keyphrase \texttt{"diet mayo (mayo diet)"} is not part of medical entity categories.
-Thus, extracting keyphrase for getting patient needs is not a trivial task.
+It is also worth to note that keyphrase \texttt{"diet mayo (mayo diet)"} is not part of any medical entity categories.
+Thus, we argue that extracting keyphrase from user-generated content especially on medical domain is not a trivial task.
 
@@
 
-\subsection{Results}
+\subsection{Results and Analyisis}
 \begin{table}
@@
 
-\subsection{Analysis}
 We performed an analysis to the aforementioned model, the result shown there are several errors.

### 2017-05-24 paper.tex
nambahin footnote Konsil

@@
 \textbf{Medical Dictionary (Md).} In our experiment, we leverage a medical knowledge base feature using a medical dictionary.
-The dictionary was built by combining disease, symptom, treatment, and drug dictionaries from \cite{skripsiKakAbid} research.
+The dictionary was built by combining disease, symptom, treatment, and drug dictionaries from Konsil Kedokteran Indonesia\footnote{www.
+kki.go.id/assets/data/arsip/SKDI_Perkonsil,_11_maret_13.pdf.}.
 The rationale behind this feature is intentions and needs of patients is more focused on their disease, symptom, treatment, and drug.

### 2017-05-25 paper.tex
Benerin Konsil
mangat

@@
 	\section{Introduction}
-Health-related or question-answering forum is becoming a trend today.
-With those forum, seeking health information and asking questions to doctors is pretty much easier.
-As a result, there is a growing need for enriching medical-related knowledge, for which it can be very valuable for several tasks in IR and NLP \cite{cao2010automatically}.
+	The growth of internet access facilitates users to share and obtain contents about healthcare topic.
+These user-generated contents are actually potential sources for enriching medical-related knowledge, for which it can be very valuable for several tasks in IR and NLP.
+
 	However, understanding those various health-related contents, especially from an online forum, is simply not a trivial task since they are written in free text format (i.e.
@@
 The work presented in this paper is absolutely in line with our goal since important keyphrases of a medical question can be used to formulate a query for the passage or question retrieval subsystem \cite{gong2009improving}.
-The following example shows the results of keyphrase extraction in a medical document:
+The following example shows the results of keyphrase extraction in a medical user-generated contents:
 	\textit{\\Dok , saya sering sekali merasa \textbf{\emph{kram pada perut kanan bagian atas}} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}.
@@
 And when the symptom occur it's \textbf{very hurt when breathing}.
-is there any connection with \textbf{moyo diet}?
+is there any connection with \textbf{mayo diet}?
 thanks before)}
@@
 
-For medical document, Sarkar and Kamal \cite{ekpMedicalDocumentHybrid} use a hybrid medical knowledge base and statistical approach to extract keyphrases from medical articles.
-They use stopwords to split candidate keyphrases, then candidates are ranked with two aspects: PF-IDF (Phrase Frequency * Inverse Document Frequency) and domain knowledge which is extracted from medical article.
+	Sarkar and Kamal \cite{ekpMedicalDocumentHybrid} use a hybrid medical knowledge base and statistical approach to extract keyphrases from medical articles.
+Stopwords was used by them  to split candidate keyphrases, then candidates are ranked with two aspects: PF-IDF (Phrase Frequency * Inverse Document Frequency) and domain knowledge which is extracted from medical article.
 
-Unfortunately, there are limited works regarding the task of keyphrase extraction from user generated on medical question, especially in Indonesian language.
-Similar research in English language has been conducted by Cao et al.
+	As far as our knowledge, there are limited works regarding the task of keyphrase extraction from user-generated contents, especially in medical question.
+Cao et al.
 \cite{cao2010automatically} use Conditional Random Fields (CRFs) for extracting keywords from medical questions in online health forum.
@@
 The dictionary was built by combining disease, symptom, treatment, and drug dictionaries from Konsil Kedokteran Indonesia\footnote{www.
-kki.go.id/assets/data/arsip/SKDI_Perkonsil,_11_maret_13.pdf.}.
+		kki.go.id/assets/data/arsip/SKDI\_Perkonsil,\_11\_maret\_13.pdf.}.
 The rationale behind this feature is intentions and needs of patients is more focused on their disease, symptom, treatment, and drug.
@@
 
-\textbf{Abbreviation and Acronym (Wa).} We also identified words by their appearance in abbreviation or acronym dictionary gathered by Abid \cite{skripsiKakAbid}.
-We observed that important word may not be shortened by the users, such as "cancer", "flu", "bell's palsy".
+	\textbf{Abbreviation and Acronym (Wa).} We also identified words by their appearance in abbreviation or acronym dictionary which was gathered manually.
+We observed that important word is rarely shortened by the users, such as "\texttt{"cancer", "flu", "bell's palsy"}.
 One-hot-vector is used to classify whether a word is an abbreviation/acronym or not.
-For example, the word "\textit{mengapa (why)}" sometimes is abbreviated to \texttt{mngp} by some patients.
 
@@
 	\textbf{Word Stickiness (Ws).} As a keyphrase, a sequence must be in a valid order.
-There is some noise such as misuse punctuation by users.
+There is some noise such as misused punctuation by users.
 For example, "\textit{Saya mengalami pusing pada jidat sakit perut dan pandangan kabur} (I am having a headache on forehead stomachache and blurred vision)", there is no comma between "jidat (forehead)", "sakit perut (stomachache)" and "dan (and)".
-Our model may mistake the sequence "(jidat sakit perut)forehead stomachache" as a keyphrase.
+Our model may mistaken the sequence "jidat sakit perut (forehead stomachache)" as a keyphrase.
 Based on that problem, we propose a feature that may capture how likely of a given word is occurred together with the word before and after.
-We use Pointwise Mutual Information (PMI) of a bigram probability to capture the likeness.
+We leveraged a language model which use Pointwise Mutual Information (PMI) of a bigram probability to capture the problem.
+The language model was trained using documents from health-related online forum.
 Formula \ref{eq:pmi} is the formula for calculating the PMI value.
@@
 	\end{equation}
-The feature function is formally described as $f_s(w) = [x, y]$ where $w$ is a word, x is the stickiness value between w and the word before, and y is the stickiness value between w and the word before.
+	The feature function is formally described as $f_s(w) = [x, y]$ where $w$ is a word in a document, $x$ is the stickiness value between $w$ and the word before, and $y$ is the stickiness value between $w$ and the word before.
 For example, the word "\texttt{cancer}" in sentence "\texttt{How to prevent cancer doc?}", the feature value is $f_s(cancer) = [0.56, 0.1]$ where $f_s$ is feature stickiness feature function.
 It is worth to note that the word "\texttt{cancer}" is rarely co-occur with the word "\texttt{doc}".
-Therefore, the stickiness value between the word "cancer" and "doc" is relatively smaller than "prevent".
+Therefore, the stickiness value between the word "\texttt{cancer}" and "\texttt{doc}" is relatively smaller than "\texttt{prevent}".
 
+	\subsection{Proposed Model}
 	We process the sequences word by word.
@@
 This approach is proven effective in sequence labeling task such as semantic role labeling \cite{SMRzhou2015end} and named entity recognition \cite{ma2016end}.
-Therefore, we utilized bi-directional LSTM (B-LSTM) for extracting structural knowledge by processing sequences both forward and backward.
-We concatenate the output from both LSTM.
+Therefore, we utilized bi-directional LSTM (B-LSTM) for extracting structural knowledge by processing sequences both forward and backward.Then, we concatenate the output from both LSTM.
 We build up to two layers of B-LSTM.
@@
 	We also experimented on customizing the way we input the features underneath our aforementioned model.
-Instead of concatenating all features into one vector, which can be seen in Formula \ref{eq:concat}, we tried to give some kind of weighting for every feature we have.
+Instead of concatenating all features into one vector, which can be seen in Formula \ref{eq:concat}, we tried to assign weights to every feature we have before the input fed into CNNs layer.
 	\begin{equation}\label{eq:concat}
@@
 Then, we removed the answer section for every pair because it is not relevant for obtaining patient intentions and needs.
+Moreover, we also observed our data and defined the definition of keyphrase on user-generated medical domain so that the annotation process can be consistent.
 Finally, we manually annotated 416 questions.
@@
 	For our experiments, we employed 10-cross-validation on our dataset.
-We use partial evaluation by Seki et al.
+We use partial evaluation which was proposed by Seki et al.
 \cite{seki2003probabilistic} to get precision, recall, F1-measure for evaluation metrics.
-This evaluation is used because we treat keyphrases as sequences of words.
+This evaluation is used because we treat keyphrases as sequences labeling task.
 
@@
 
-For comparison, we implemented RAKE \cite{rake} and CRF \cite{cao2010automatically}, which use unsupervised and supervised approach.
-For CRF, we use the same features proposed above.
-We also conducted an experiment to proof the effectiveness of our CNN layer by comTM with CNNs layer(CNN-B-LSTM).
-Furthermore, we also compared our model with or without weighting layer (W-CNN-B-LSTM).
+	For comparison, we implemented RAKE \cite{rake} and CRF \cite{cao2010automatically}.
+For CRF, we use the same features as proposed above.
+Moreover, We also conducted an experiment to proof the effectiveness of our CNNs layer by comparing B-LSTM with (CNN-B-LSTM) or without CNNs layer.
+We also compared our model with (W-CNN-B-LSTM) or without weighting layer.
 
-As we can see in Table \ref{tab:model_scenario}, RAKE and CRF underperformed on Indonesian user-generated medical question since RAKE were specially devised for formal text.
+	As we can see in Table \ref{tab:model_scenario}, RAKE performed the worst on Indonesian user-generated medical question since RAKE were specially devised for formal text.
+Of the other methods, CRF performed the worst.
 For CRF, based on our observation from the result provided by CRF, the method failed to predict long sequences as a keyphrase.
@@
 Moreover, our weighting layer shows improvement compared to CNN-B-LSTM.
-Hence, the best result is obtained by W-CNN-LSTM.
+Hence, the best result was obtained by W-CNN-LSTM.
+This is indicated that the feature weighting process worked well and could to some degree demonstrate the effectiveness of our model in keyphrase extraction for user-generated medical domain.
 
@@
 Some of the error are uncompleted keyphrases.
-For example, "pusing pada (headache on)", "obat untuk (medicine for)".
+For example, "\texttt{pusing pada (headache on)}", "\texttt{obat untuk (medicine for)}".
 Our model also failed to capture complex medicine name and disease.
@@
 Moreover, there are also special case that our model failed to handle.
-For example, "penyembuhan untuk sakit kepala dan tenggorokan (treatment for headache and sore throat)", the keyphrase need to be captured as a whole because "sore throat" have a connection with the word "treatment".
-But our model failed to capture that connection and extracted "treatment for headache" and "sore throat" separately instead.
+For example, "\texttt{penyembuhan untuk sakit kepala dan tenggorokan (treatment for headache and sore throat)}", the keyphrase need to be captured as a whole because "\texttt{sore throat}" have a connection with the term "treatment for".
+But, our model failed to capture that connection and extracted "treatment for headache" and "sore throat" separately instead.
 	\iffalse
@@
 	\section{Conclusion}
-We have proposed a model to address the task of keyphrase extraction on Indonesian user-generated medical domain.
+	We have proposed a model to address the task of keyphrase extraction on Indonesian user-generated contents in medical domain.
 Extracting information patient intentions and needs on user-generated medical contents is not a trivial task due to the fact that the content is usually short, contain many medical terms, and written in an unstructured format, as opposed to formal text.
